---
title: "Quiz 4"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(kableExtra)
```
<style>body{text-align: justify}</style>
### 1.

```{r q1}
question("Suppose you want to construct a confidence interval for a population proportion. Which of the following,
         if it were true, would prevent you from being able to assume that the distribution of the sample
         proportion is nearly normal?",
         answer("n = 104. Out of these 104 there are only a few successes (15), 
                but relatively many failures (89)."),
         answer("n = 104. Out of these 104 there are an equal number of successes and failures (52 each)."),
         answer("None of these options.",correct = TRUE),
         answer("n = 104. These observations are a simple random sample and make up less than 10% of the
                population."))
```

### 2.

```{r q2}
question("When performing a hypothesis test on proportions (either where $\\mathcal{H}_0:p = p_0$ or where 
         $\\mathcal{H}_0:p_1=p_2$) you should use the observed number of successes and failures when 
         checking conditions.",
         answer("TRUE"),
         answer("FALSE",correct = TRUE),
         answer("Depend on the context"),
         answer("Observed proportion for one sample, expected proportion for two samples."))
```

### 3.

```{r q3}
question("You are tasked with conducting a hypothesis test evaluating whether a majority or minority of Americans 
         think it was a bad decision to hold the 2014 winter games in Russia. You’re going to use data from a 2014 
         Pew Research poll asked 1,003 Americans this question, and 44% responded yes. Which of the following is 
         the correct set of hypotheses?",
         answer("$\\mathcal{H}_0 :p = 0.5,\\mathcal{H}_A :p < 0.5$"),
         answer("$\\mathcal{H}_0 :p = 0.33,\\mathcal{H}_A :p \\neq 0.44$"),
         answer("$\\mathcal{H}_0 :p = 0.5,\\mathcal{H}_A :p \\neq 0.5$",correct = TRUE),
         answer("$\\mathcal{H}_0 :p = 0.5,\\mathcal{H}_A :p \\neq 0.44$"))
```

### 4.

```{r q4}
question("The campaign manager for a congressional candidate claims that the candidate has more than 50% support
         from the district’s electorate. A newspaper collects a simple random sample of 500 likely voters in this
         district and estimates the support for this candidate to be 52%. The p-value for the hypothesis test
         evaluating the campaign manager’s claim is 0.19. Which of the below is correct?",
         answer("If in fact 50% of likely voters support this candidate, the probability of obtaining a random 
         sample of 500 likely voters where 52% or more support the candidate is 0.19.",correct = TRUE),
         answer("95% of random samples of size 500 will estimate the support for this candidate to be 52%."),
         answer("The success-failure condition is not met, so this p-value is not reliable."),
         answer("The data provide convincing evidence for the campaign manager’s claim."))
```

### 5.

<b>Voters in the U.S. state of New Jersey voted on a measure that would legalize sports betting. Before the vote,
SurveyUSA asked a random sample of registered voters the following question: “’If betting on sports were to become
legal in New Jersey, would you yourself place bets?” The distribution of responses by age group is shown in the
table below. Consider a hypothesis test evaluating whether there is a difference between proportions of 18 to 34
year olds and 35+ year olds who would never place bets. Using the information from the table, calculate the
standard error for this hypothesis test. 

```{r q5table}
d <- data.frame(x1 = c(3,69,71,1,144),x2 = c(30,128,224,7,389),x3 = c(33,197,295,8,533),
                row.names = c("regularly","occasionaly","never","not sure","total"))
names(d) <- c("18 to 34","35+","total")
kable(d,longtable = T,booktabs = T) %>% add_header_above(c("","age group" = 2,"")) %>%
  column_spec(1:4, width = "8em") %>% pack_rows("response",1,4,
                                                label_row_css = "background-color:#216;color: #fff;")
```

```{r q5a,exercise = TRUE}
## make calculations here

```

```{r q5a-solution}
## make calculations here
p1 <- 71/144
p2 <- 224/389
sqrt(p1*(1-p1)/144 + p2*(1-p2)/389)
```

```{r q5}
question("Choose the closest answer",
         answer("0.4931"),
         answer("0.0024"),
         answer("0.5535"),
         answer("0.0486",correct = TRUE),
         answer("0.5758"))
```

### 6.

<b>To evaluate the following hypotheses</b>
<center>
$\mathcal{H}_0:p = 0.3\\\mathcal{H}_{A} :p \neq 0.3$
</center>
we use a random sample of 50 observations where $\hat{p}=0.36$. Which of the following is the correct standard 
error? 

```{r q6a,exercise = TRUE}
## make calculations here

```

```{r q6}
question("Choose the closest answer.",
         answer("0.0297"),answer("0.0042"),answer("0.0648",correct = TRUE),
         answer("0.0679"),answer("0.0092"),answer("0.0096"))
```

```{r q6a-solution}
sqrt(0.7*0.3/50)
```

### 7.

<b>At the beginning of a semester an anonymous survey was conducted on students in a statistics class. Two of the 
questions on the survey were about gender and whether or not students have equal, more, or less energy in the 
afternoon compared to the morning. Below are the results.</b>

|      |Equal|Less |More  |
|:-----|----:|----:|-----:|
|Female|18   |37   |24    |
|Male  |9    |15   |24    |


```{r q7}
question("What test should we perform to see if gender and energy level are associated?",
         answer("Comparing two proportions"),
         answer("hypothesis test for a single mean"),
         answer("Chi-square test of goodness of fit"),
         answer("F test"),
         answer("Comparing two means"),
         answer("Z test"),
         answer("Chi-square test of independence",correct = TRUE),
         answer("ANOVA"))
```

### 8.

```{r q8}
question("A report on your local TV news station claims that 60% of the city’s residents support using limited city
         funds to hire and train more police officers. A second local news station has picked up this story, and
         they claim that certainly less than 60% of residents support the additional hiring. In order to test this
         claim the second news station takes a random sample of 100 residents and finds that 56 of them (56%)
         support the use of limited funds to hire additional police officers. Which of the following is the correct
         set-up for calculating the p-value for this test?",
         answer("Randomly sample 100 residents of a nearby city, and record the number of residents in the sample 
         who support the hiring of additional police officers. Repeat this many times and calculate the proportion 
         of samples where at least 56% of the residents support the hiring."),
         answer("Roll a 10-sided die 100 times and record the proportion of times you get a 6 or lower. Repeat this
         many times, and calculate the number of simulations where the sample proportion is 60% or less."),
         answer("In a bag place 100 chips, 56 red and 44 blue. Randomly sample 100 chips, with replacement, and 
         record the proportion of red chips in the sample. Repeat this many times, and calculate the proportion of 
         samples where at least 60% of the chips are red."),
         answer("Roll a 10-sided die 100 times and record the proportion of times you get a 6 or lower. Repeat this
         many times, and calculate the number of simulations where the sample proportion is 56% or less.",
         correct = TRUE))
```

### 9.

<b>One of the early studies linking smoking and lung cancer compared patients hospitalized with lung cancer to
similar patients without lung cancer (hospitalized for other reasons), and recorded whether each patient smoked. For
a hypothesis test testing whether the proportion of smokers is higher for the patients with lung cancer than for
patients without lung cancer, the p-value is less than 0.000001.</b>


```{r q9table}
d <- data.frame(smoker = c(647,622,1269),nonsmoker = c(2,27,29),total = c(649,649,1298),
                row.names = c("lung cancer","not sure","total"))
kable(d,longtable = T,booktabs = T) %>% add_header_above(c("","smoking status" = 2,"")) %>% 
  column_spec(1:4, width = "8em") 
```

```{r q9a,exercise = TRUE}
## Make computations here if needed
```
```{r q9}
question("Does this provide significant evidence that smoking causes lung cancer?",
        answer("Whether or not we can conclude that smoking causes lung cancer depends on the statistical method 
        the researchers used to obtain the p-value."),
        answer("Based on this study we cannot conclude that smoking causes lung cancer, regardless of the 
               p-value.",correct = TRUE),
        answer("Yes, with the given p-value we would reject $\\mathcal{H}_0$ in favor of 
        $\\mathcal{H}_A$, and conclude that smoking causes lung cancer."),
        answer("No, with the given p-value we would fail to reject $\\mathcal{H}_0$ in favor of 
               $\\mathcal{H}_A$."))
```

### 10.

```{r q10}
question("80% of Americans start the day with a cereal breakfast. Based on this information, determine if the      
         following statement is true or false.
         “The sampling distribution of the proportions of Americans who start the day with a cereal breakfast in 
         random samples of size 40 is right skewed.”",answer("TRUE"),answer("FALSE",correct = TRUE))
```


### 11.

<b>At a stop sign, some drivers come to a full stop, some come to a ‘rolling stop’ (not a full stop, but slow down),
and some do not stop at all. We would like to test if there is an association between gender and type of stop (full,
rolling, or no stop). We collect data by standing a few feet from a stop sign and taking note of type of stop and 
the gender of the driver. Below is a contingency table summarizing the data we collected. If gender is not 
associated with type of stop, how many males would we expect to not stop at all? </b>

<center>
```{r table11}
d <- data.frame(female = c(6,16,4),male = c(6,15,3),row.names = c("full stop","rolling stop","no stop"))
kable(d,longtable = T,booktabs = T) %>% add_header_above(c("","gender" = 2)) %>% 
  column_spec(2:3, width = "5em") %>% pack_rows("stop",1,3,label_row_css = "background-color:#216;
                                                color: #fff;")
```
</center>

```{r q11a,exercise = TRUE}
# make computations here

```

```{r q11}
question("Choose the closest answer.",answer("3.64"),answer("6.24"),answer("5.76"),answer("3.36",correct = TRUE))
```

```{r q11a-solution}
(6 + 15 + 3) * (4 + 3) / (6 + 6 + 16 + 15 + 4 + 3)
```

### 12.

```{r q12}
question("True / False: A randomization test for $H_0:p_1=p_2$ uses a randomization distribution centered at     
         0.",answer("TRUE",correct = TRUE),answer("FALSE"))
```