---
title: "Quiz 1"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include = FALSE}
library(learnr)
library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
gradethis_setup()
```
<style>body{text-align: justify}</style>
### 1.

<b>Consider the table below describing a data set of individuals who have registered to volunteer
at a public school.</b>

|Name |Year born|Phone number|Number of siblings|Annual Income|
|:----|:--------|:-----------|:----------------:|:-----------:|
|Jenny|1975     |8929223     |0                 |60,000       |
|Ted  |1984     |8675309     |3                 |22,500       |
|...  |...      |...         |...               |...          |


```{r q1}
question("Which of the choices below lists categorical variables?",
         answer("phone number and name",correct = TRUE),
         answer("name and number of siblings"),
         answer("annual income and phone number"),
         answer("number of siblings and year born"))
```

### 2.

```{r q2}
question("A study is designed to test the effect of type of light on exam performance of
         students. 180 students are randomly assigned to three classrooms: one that is dimly lit,
         another with yellow lighting, and a third with white fluorescent lighting, and given the
         same exam. Which of the following correctly identifies the variables used in the study
         as explanatory and response?",
         answer("explanatory: exam performance</br>
         response: dimly lit, yellow, white fluorescent"),
         answer("explanatory: exam performance</br>
         response: type of light (categorical with 3 levels)"),
         answer("explanatory: dimly lit, yellow, white fluorescent</br>
         response: exam performance"),
         answer("explanatory: type of light (categorical with 3 levels)</br>
         response: exam performance",correct = TRUE))
```

### 3.

```{r q3}
question("Past research suggests that students who study with fewer distractions (internet, cell 
         phone, etc.) tend to get higher grades. Which of the following is the best scenario for 
         being able to generalize this finding to the population of all students?",
         answer("The students participate in the study after seeing signs about the survey posted
         around campus."),
         answer("A survey is emailed to all registered students, and the results are based on the
         sample of returned surveys."),
         answer("Sample only includes students who are in classes that the researcher teaches."),
         answer("A student list for the college is obtained and students are randomly selected 
         from the list, and all selected students participate in the study.",correct = TRUE))
```

### 4.

<b>An extraneous variable that is related to the explanatory and response variables and
that prevents us from deducing causal relationships based on observational studies is
called a _______ (use all lower cases in your answer please).</b>

```{r q4,exercise = TRUE}
## Enter word here as a string

```

```{r q4-check}
grade_result(
  pass_if(~identical(tolower(.result),'confounding'))
)
```

### 5.

```{r q5}
question("For your political science class, you’d like to take a survey from a sample of all the
         Catholic Church members in your town. Your town is divided into 17 neighborhoods, each
         with similar socio-economic status distribution and ethnic diversity, and each contains
         a Catholic Church. Rather than trying to obtain a list of all members of all these
         churches, you decide to pick 3 churches at random. For these churches, you’ll ask to get
         a list of all current members and contact 100 members at random. What kind of design
         have you used?",
         answer("simple random sampling"),
         answer("multistage sampling",correct = TRUE),
         answer("stratified sampling"),
         answer("quota sampling"),
         answer("systematic sampling"))
```

### 6.

```{r q6}
question("Which of the following is not one of the four principles of experimental design?",
         answer("block"),
         answer("control"),
         answer("replicate"),
         answer("cluster",correct = TRUE))
```

### 7.

```{r q7}
question("Which of the following is one of the four principles of experimental design?",
         answer("randomize",correct = TRUE),
         answer("stratify"),
         answer("cluster"))
```