---
title: "Capstone Quiz I"
output: statsr:::statswithr_lab
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  comment = '', fig.width = 6, fig.height = 6,fig.align = 'center'
)
```

This initial quiz will concern exploratory data analysis (EDA) of the Ames Housing dataset.  
EDA is essential when working with any source of data and helps inform modeling.

First, let us load the data:

```{r load}
load("ames_train.Rdata")
```


1. Which of the following are the three variables with the highest number of missing observations?

<ol>
<li> `Misc.Feature`, `Fence`, `Pool.QC` </li>
<li> <text style="color:red">`Misc.Feature`, `Alley`, `Pool.QC`</text> </li> 
<li> `Pool.QC`, `Alley`, `Fence` </li> 
<li> `Fireplace.Qu`, `Pool.QC`, `Lot.Frontage` </li>
</ol>

```{r Q1}
# type your code for Question 1 here, and Knit
names(sort(apply(apply(ames_train,2,is.na),2,sum),TRUE))[1:3]
```

2. How many categorical variables are coded in R as having type `int`?  Change them to factors 
when conducting your analysis.

<ol>
<li> 0 </li>
<li> 1 </li>
<li> <text style="color:red">2</text></li>
<li> 3 </li>
</ol>

```{r Q2}
# type your code for Question 2 here, and Knit
str(ames_train)
ames_train$Overall.Qual <- factor(ames_train$Overall.Qual,ordered = TRUE)
ames_train$Overall.Cond <- factor(ames_train$Overall.Cond,ordered = TRUE)
```

3. In terms of price, which neighborhood has the highest standard deviation?  

<ol>
<li> <text style="color:red">`StoneBr`</text></li>
<li> `Timber` </li>
<li> `Veenker`</li>
<li> `NridgHt`</li>
</ol>

```{r Q3}
# type your code for Question 3 here, and Knit
library(dplyr,warn.conflicts = F)
ames_train %>% group_by(Neighborhood) %>% summarize(sd = sd(price)) %>% arrange(desc(sd)) %>% head(1)
```

4. Using scatter plots or other graphical displays, which of the following variables appears to be the 
best single predictor of `price`?

<ol>
<li> `Lot.Area`</li>
<li> `Bedroom.AbvGr`</li>
<li> <text style="color:red">`Overall.Qual`</text></li>
<li> `Year.Built`</li>
</ol>

```{r Q4}
# type your code for Question 4 here, and Knit
par(mfrow = c(2,2))
with(ames_train,plot(Lot.Area,price,pch = 19,col = rgb(.6,0,.4,.5)))
with(ames_train,plot(Bedroom.AbvGr,price,pch = 19,col = rgb(.6,0,.4,.5)))
with(ames_train,plot(as.numeric(Overall.Qual),price,pch = 19,col = rgb(.6,0,.4,.5)))
with(ames_train,plot(Year.Built,price,pch = 19,col = rgb(.6,0,.4,.5)))
```

5. Suppose you are examining the relationship between `price` and `area`.  Which of the following
variable transformations makes the relationship appear to be the most linear?

<ol>
<li> Do not transform either `price` or `area`</li>
<li> Log-transform `price` but not `area`</li>
<li> Log-transform `area` but not `price`</li>
<li> <text style="color:red">Log-transform both `price` and `area`</text></li>
</ol>

```{r Q5}
# type your code for Question 5 here, and Knit
par(mfrow = c(2,2))
with(ames_train,plot(area,price))
with(ames_train,plot(area,log(price)))
with(ames_train,plot(log(area),price))
with(ames_train,plot(log(area),log(price)))
```

6. Suppose that your prior for the proportion of houses that have at least one garage is Beta(9, 1). 
What is your posterior? Assume a beta-binomial model for this proportion.

<ol>
<li> Beta(954, 46)</li>
<li> Beta(963, 46)</li>
<li> Beta(954, 47)</li>
<li> <text style = "color:red">Beta(963, 47)</text></li>
</ol>

```{r Q6}
# type your code for Question 6 here, and Knit
x <- ames_train %>% filter(Garage.Cars >= 1) %>% summarise(Garage.Cars.ge1=n())
n <- ames_train %>% filter(!is.na(Garage.Cars)) %>% summarise(Garage.Cars.ge1=n())
paste("Beta(",9 + x,",",1 + n - x,")",sep = '')
```

7. Which of the following statements is true about the dataset?

<ol>
<li> Over 30 percent of houses were built after the year 1999.</li>
<li> The median housing price is greater than the mean housing price.</li>
<li> <text style="color:red">21 houses do not have a basement.</text></li>
<li> 4 houses are located on gravel streets.</li>
</ol>

```{r Q7}
# type your code for Question 7 here, and Knit
quantile(ames_train$Year.Built,seq(0,1,0.1))
median(ames_train$price) > mean(ames_train$price)
ames_train %>% select(Total.Bsmt.SF) %>% filter(Total.Bsmt.SF == 0)  %>% summarise(count = n())
table(ames_train$Street)
```

8. Test, at the $\alpha = 0.05$ level, whether homes with a garage have larger square 
footage than those without a garage.

<ol>
<li> <text style="color:red">With a p-value near 0.000, we reject the null hypothesis of no difference.</text></li>
<li> With a p-value of approximately 0.032, we reject the null hypothesis of no difference.</li>
<li> With a p-value of approximately 0.135, we fail to reject the null hypothesis of no difference.</li>
<li> With a p-value of approximately 0.343, we fail to reject the null hypothesis of no difference.</li>
</ol>

```{r Q8}
# type your code for Question 8 here, and Knit
ames_train$has_garage <- ifelse(ames_train$Garage.Area > 0 ,"yes","no")
round(t.test(area ~ has_garage,ames_train,paires = F,var.equal = F)$p.value,2)
```

9. For homes with square footage greater than 2000, assume that the number of bedrooms above ground follows 
a Poisson distribution with rate $\lambda$.  Your prior on $\lambda$ follows a Gamma distribution with mean 
3 and standard deviation 1.  What is your posterior mean and standard deviation for the average number of 
bedrooms in houses with square footage greater than 2000 square feet?

<ol> 
<li> Mean: 3.61, SD: 0.11</li>
<li> <text style="color:red">Mean: 3.62, SD: 0.16</text></li>
<li> Mean: 3.63, SD: 0.09</li>
<li> Mean: 3.63, SD: 0.91</li>
</ol>

```{r Q9}
# type your code for Question 9 here, and Knit
lambda       <- 3
sigma_prior  <- 1
b <- lambda / sigma_prior
a <- lambda * b
x <- ames_train %>% filter(area>2000) %>% summarise(x = sum(Bedroom.AbvGr))
n <- ames_train %>% filter(area>2000) %>% summarise(n = n())
a_post <- a + x
b_post <- b + n
lambda_post <- a_post / b_post
sigma_post <- sqrt(a_post / b_post^2)
paste("Mean: ",round(lambda_post,2),", SD: ",round(sigma_post,2),sep = '')
```

10. When regressing $\log$(`price`) on $\log$(`area`), there are some outliers.  Which of
the following do the three most outlying points have in common?

<ol> 
<li> They had abnormal sale conditions.</li>
<li> They have only two bedrooms.</li>
<li> They have an overall quality of less than 3.</li>
<li> <text style="color:red">They were built before 1930.</text></li>
</ol>

```{r Q10}
# type your code for Question 10 here, and Knit
fit <- lm(log(price) ~ log(area),data = ames_train)
plot(fit,1)
for (x in c(428,741,206)) print(ames_train$Year.Built[x])
```

11. Which of the following are reasons to log-transform `price` if used as a dependent variable in a linear regression?
<ol> 
<li> `price` is right-skewed.</li>
<li> `price` cannot take on negative values.</li>
<li> `price` can only take on integer values.</li>
<li> <text style="color:red">Both a and b.</text></li>
</ol>

```{r Q11}
# type your code for Question 11 here, and Knit
hist(ames_train$price)
```

12. How many neighborhoods consist of only single-family homes? (e.g. `Bldg.Type` = `1Fam`)

<ol> 
<li> 0</li>
<li> 1</li>
<li> 2</li>
<li> <text style="color:red">3</text></li>
</ol>

```{r Q12}
# type your code for Question 12 here, and Knit
ames_train %>% group_by(Neighborhood) %>% summarize(mu = mean(Bldg.Type == "1Fam")) %>% 
  filter(mu == 1) %>% summarise(n())
```

13. Using color, different plotting symbols, conditioning plots, etc., does there appear to 
be an association between $\log$(`area`) and the number of bedrooms above ground (`Bedroom.AbvGr`)? 

<ol> 
<li> <text style="color:red">Yes</text></li>
<li> No </li>
</ol>

```{r Q13}
# type your code for Question 13 here, and Knit
with(ames_train,plot(Bedroom.AbvGr,log(area)))
```

14. Of the people who have unfinished basements, what is the average square footage of
the unfinished basement?

<ol> 
<li> 590.36</li>
<li> <text style="color:red">595.25</text></li>
<li> 614.37</li>
<li> 681.94</li>
</ol>

```{r Q14}
# type your code for Question 14 here, and Knit
ames_train %>% filter(!is.na(Bsmt.Unf.SF),Bsmt.Unf.SF > 0) %>% summarise(mu = round(mean(Bsmt.Unf.SF),2))
```