---
title: "Exploring the BRFSS data"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: journal
    toc: true
---
<style>body{text-align: justify}</style>
## Setup

### Load packages

```{r load-packages, message = FALSE,comment = ''}
library(ggplot2)
library(dplyr)
## R version
library(grid)
library(gridExtra)
library(ggmosaic)
library(scatterplot3d)
library(RColorBrewer)
getRversion()
```

### Load data

```{r load-data,cache = TRUE}
load("brfss2013.RData")
```

## Part 1: Data

### Introduction

The data we have loaded is stored in variable 'brfss2013', it contains 491775 
observations and 330 variables. The Behavioral Risk Factor Surveillance System (BRFSS) is
a collaborative project between all of the states in the United States (US) and
participating US territories and the Centers for Disease Control and Prevention (CDC).
The BRFSS was initiated in 1984, with 15 states collecting surveillance data on risk
behaviors through monthly telephone interviews. Over time, the number of states
participating in the survey increased; by 2001, 50 states, the District of Columbia,
Puerto Rico, Guam, and the US Virgin Islands were participating in the BRFSS. Today, all
50 states, the District of Columbia, Puerto Rico, and Guam collect data annually and
American Samoa, Federated States of Micronesia, and Palau collect survey data over a
limited point-in-time (usually one to three months). In this document, the term “state”
is used to refer to all areas participating in BRFSS, including the District of Columbia,
Guam, and the Commonwealth of Puerto Rico.

### Concerns On Data Collection

In this report we will briefly explore three simple questions based on the data we 
loaded. A big concern according to the introduction is the _no response_ bias, since 
many interviewers might not respond to the call or refuse to answer, which might also
imply a _volunteer response_ bias in the collection of data e.g. someone might want to
keep the personal health record private and another healthier person might want to 
demonstrate a healthy life style by being willing to answer the call. We also don't know 
how diverse the socioeconomic status of the subjects is, except from some indicators like
"rent" or "home status" or "health insurance coverage". Having the above remarks in mind 
we will treat the states as homogeneous within and heterogeneous between all others, 
justifying it by noting that each state follows different policies and has a diverse 
economy from the others i.e. Alaska has big income from oil sources, California has the 
hollywood show industry etc with different opportunities and job diversity within the 
USA.

### Stratified Sampling

We will randomly sample 3 states and then sample from each strata 1000 observations, the 
process will create three distinct datasets in order to conduct the exploratory analysis
and make the findings of the analysis more robust and generalizable. 
We will set the seed in order to make the report reproducible.

```{r data creation}
set.seed(88)
```

## Part 2: Research questions

<b><u>Research question 1:</b></u>

Is there any connection between __time of sleep__ and the __reported weight__ in 
pounds? Is weight and time of sleep connected to __sex__ or __depressive disorder__ in
for them to be considered as blocking factors further analysis?

<b><u>Research question 2:</b></u>

How does smoking at least 100 cigarettes affect the probability of suffering a stroke? 
Are there any other concerns for similar cardiovascular problems caused by the smoking 
habit of even a small amount of cigarettes?

<b><u>Research quesτion 3:</b></u>

Does a positive diabetes diagnosis of a subject, enforces a change in life style? How
does the knowledge of having diabetes by a subject, affects the hours of exercising and
further connected to that how does this affect the overall health and change in nutrition
habits of a subject positively or negatively?

## Part 3: Exploratory data analysis

### Research quesion 1:

We will investigate the response variable <text style="red">reported weight</text> (in 
pounds) against the __time of sleep__ (in hours) and the __confounding__ variables 
__sex__ and __depression__ status.

```{r dataset1}
states <- unique(brfss2013$X_state)
dataset1 <- brfss2013 %>% 
  filter(X_state %in% sample(states,3,replace = FALSE)) 
dataset1 <- dataset1[c('sleptim1','weight2','addepev2','sex')] %>% 
  mutate(weight2 = as.numeric(weight2),sleptim1 = as.numeric(sleptim1))
dataset1 <- dataset1[complete.cases(dataset1),] %>% filter(sleptim1 != '',
    weight2 != '.b',weight2 != ',')
```

We prepared the data set and now we will have to identify the variables we will use,
these are `sleptim1`, `weight2` and `addepev2`. Since gender plays a role in 
weight and body mass index we might consider using the `sex` variable too. 

```{r graphs1,fig.align = 'center'}
colors <- c(rgb(1,0,0,0.4),rgb(0,0,1,0.4))
colScale1 <- scale_colour_manual(name = "sex",values = colors)
names(colScale1) <- levels(as.vector(dataset1$sex))
g1 <- ggplot(data = dataset1,aes(x = sleptim1,y = weight2,colour = sex)) + 
  geom_point() + geom_smooth(method = 'lm',formula = y ~ x,
                             color = 'black',lwd = 2) + colScale1 +
  scale_y_continuous(name = "Weight In Pounds", limits = c(0, 600)) +
  geom_smooth(formula = y ~ splines::bs(x,3),method = "gam") 
colScale2 <- scale_colour_manual(name = "depression status",values = colors)
names(colScale2) <- levels(as.vector(dataset1$addepev2))
g2 <- ggplot(data = dataset1,aes(x = sleptim1,y = weight2,colour = addepev2)) + 
  geom_point() + geom_smooth(method = 'lm',formula = y ~ x,
                             color = 'black',lwd = 2) + colScale2 +
  scale_y_continuous(name = "Weight In Pounds", limits = c(0, 600)) +
  geom_smooth(formula = y ~ splines::bs(x,3),method = "gam")
grid.arrange(g1,g2,ncol = 2,top = textGrob("Color By Factor - Sex/Depression"))
```

As expected, the left plot shows that gender plays a role in weight, regardless of the 
time a subject sleeps and that men as expected are heavier. The bulk of the observations 
lies between 4 to 12 hours, in which we see the interesting pattern of women's weight 
dominating the bottom and the outliers' area leaving the middle area dominated by men. In
the right plot as expected the 'no depression' state is prominent and we don't see any 
specific pattern of the red spots, which are scattered as if they were positioned
randomly on top of the blue dots. So our investigation should consider __sex__ as a
confounding variable, regardless of the ratio of males to females which is less than one
and the fact that the depressed people are underrepresented, since in the left plot we 
observe a pattern and in the second none. The ratios mentioned can be computed with 

```{r ratios,comment = ""}
table(dataset1$sex)
table(dataset1$addepev2)
```

and we conclude that in the next steps of inference and experimentation, __sex__ 
should be considered as a blocking factor.

### Research quesion 2:

For this question we will create a simple model in which the explanatory variable is 
whether the subject smoked at least 100 cigarettes or not and the response variable is 
whether the subject suffered a stroke or not. We will prepare the dataset which will 
be used in this section.

```{r dataset2}
dataset2 <- brfss2013 %>%
  filter(X_state %in% sample(states,3,replace = FALSE)) 
```

The response variable in dataset2 is __smoke100__ and the explanatory variable is 
__cvdstrk3__. For this question we cannot do nothing more than conducting an
observational analysis, we have two categorical variables and hence a mosaic plot fits 
the nature of the question. In order to make our exploratory analysis more robust, we
might also be interested in another variable with the name
__cvdinfr4__, which is a binary factor of whether a subject suffered a heart attack in 
the past. So combining those two factors we might observe a connection between smoking 
few cigarettes and cardiovascular problems represented by two variables combined in the 
x axis.

```{r graphs2,fig.align = "center"}
ggplot(data = dataset2) + geom_mosaic(aes(x = product(smoke100),fill = smoke100,
      conds = product(cvdinfr4,cvdstrk3)),divider = c("vspine","hspine","hspine")) + 
  labs(y = 'smoked over 100 cigarettes',
       x = 'diagnosed stroke:heart attack') + ggtitle("Conditional Mosaic Plot") + 
  theme_bw()
```

We see that a non negligible amount of area is colored in red, which provides a good 
observational evidence of whether even a small amount of cigarettes raises the risk of 
health damage by stroke or heart attack.

### Research quesion 3:

We will prepare the dataset.

```{r dataset3}
dataset3 <- brfss2013 %>%
  filter(X_state %in% sample(states,3,replace = FALSE))
dataset3 <- dataset3 %>% select(diabete3,exerhmm1,fruitju1,fruit1,fvbeans,fvgreen,
                                fvorang,vegetab1,avedrnk2)
dataset3 <- dataset3[complete.cases(dataset3),]
```

We will use __diabete3__ variable which records the status of a subject regarding
diabetes, as a <text style="red">blocking factor</text> to sequentially explore the
connection of the disease with training, nutrition and alcohol consumption habits.

####  Diabetes And Exercise

__exerhmm__: Minutes Or Hours Walking, Running, Jogging, Or Swimming 

```{r graphs3a,fig.align = "center"}
ggplot(data = dataset3) + geom_boxplot(aes(y = diabete3,x = exerhmm1)) + theme_bw()
```

We know that some women during pregnancy can develop diabetes for a short time and we 
will not be concerned with that box. For the other cases there doesn't seem to be any  
median and quantile difference between the status Yes/No, except from the outliers which 
might be attributed to noise and difference in class sizes.

#### Diabetes / Fruit-Juice Consuption

__fruitju1__: How Many Times Did You Drink 100 Percent Pure Fruit Juices?
__fruit1__  : How Many Times Did You Eat Fruit?

```{r graphs3b,fig.align = 'center'}
colors <- brewer.pal(4,"RdYlBu")
colScale1 <- scale_colour_manual(name = "diabetes status",values = colors)
names(colScale1) <- levels(as.vector(dataset1$sex))
ggplot(data = dataset3) + geom_point(aes(x = fruitju1,y = fruit1,color = diabete3)) + 
  colScale1
```

We don't observe any specific trend of clustering between the Yes/No diabetes status.

#### Diabetes/ Vegetable - Beans Consumption

__fvbeans__: How Many Times Did You Eat Beans Or Lentils?

__fvgreen__: How Many Times Did You Eat Dark Green Vegetables?

__fvorang__: How Many Times Did You Eat Orange-Colored Vegetables?

__vegetab1__: How Many Times Did You Eat Other Vegetables?

```{r graphs3c,fig.align = 'center'}
par(mfrow = c(1,2))
scatterplot3d(x = dataset3$fvbeans, y = dataset3$fvgreen,
                             z = dataset3$fvorang,
                             color = colors[dataset3$diabete3],pch = 19)
scatterplot3d(x = dataset3$fvbeans, y = dataset3$fvgreen,
                             z = dataset3$vegetab1,
                             color = colors[dataset3$diabete3],pch = 19)
```

We observe the red points (diabetes diagnosed subjects) shifting to the right top bottom 
corner, which imply that a further investigation is needed to analyze the relationship   
between developing low fat/sugar after being diagnosed with diabetes implying that people
take their health seriously.

#### Diabetes / Alcohol Consumption Reduction

__avedrnk2__: Avg Alcoholic Drinks Per Day In Past 30

```{r graphs 3d,fig.align =  'center'}
ggplot(data = dataset3) + geom_boxplot(aes(x = avedrnk2,y = diabete3))
```

Although the interquantile ranges don't show differences, the median of alcohol
consumption of subjects with diabetes is a little lower than the other boxes, which
implies that those subjects lower the consumption of drinks adopting a healthier life 
style and could be added as evidence of a need for further investigation for how
seriously diabetics take their health condition.