---
title: "Statistical inference with the GSS data"
author: "George Papadopoulos</br>pgeorgios8@gmail.com"
output: 
  html_document: 
    css: style.css
    fig_height: 4
    highlight: pygments
    theme: spacelab
    toc: true
---
<style>body{text-align: justify}</style>
## Setup

### Load packages

Packages loaded, R version and date.

```{r load-packages, message = FALSE,comment = ''}
library(ggplot2)
library(dplyr,warn.conflicts = F)
library(gridExtra)
getRversion()
Sys.Date()
```

## Part 1: Data

### Intoduction

As a beginning of a series of statistical investigations which are conducted to test various 
socioeconomic changes and diversifications between different social stratums of income and educational 
background, in this report we will investigate a hypothesis for a specific section of the data for a 
specific year.

The Behavioral Risk Factor Surveillance System (BRFSS) is the nation’s premier system of health-related
telephone surveys that collect state data about U.S. residents regarding their health-related risk
behaviors, chronic health conditions, and use of preventive services. Established in 1984 with 15 states,
BRFSS now collects data in all 50 states as well as the District of Columbia and three U.S. territories.
BRFSS completes more than 400,000 adult interviews each year, making it the largest continuously conducted
health survey system in the world.

The issues and concerns raised from the methodology being used to gather information are 

* No response bias: Individuals without a landline or cellphone or who refuse to respond to or participate
in phone surveys or who are unavailable/unreachable by phone for the survey at the time it was being
conducted.

* Response bias: 
  1. Overreporting/Underreporting desirable behaviors and/or traits and/or exaggerating or 
  misrepresenting 
  certain traits, such as heigh, education, or income.
  2. Inaccurately providing information i.e. how many hours did you watch TV in the last week?
  3. Potentially being inconsistent in interview practices and question sets between the participating 
  state agencies.
  4. Personal beliefs which might contaminate the data i.e. someone who does not want to admit that he 
  doesn't like equal pay for the same job between different races and blame the people for not educating 
  themselves better.

```{r data load}
load("gss.Rdata")
```

The data consists of 57061 observations of 114 variables. __Press the show button!__

<input type=button class=hideshow>
```{r summary,echo = FALSE,comment = ''}
summary(gss)
```
</input>

Most of the variables are categorical with many of them having binary inputs _Yes or No_.

## Part 2: Research question

We will focus our interest in the following variables.

* helppoor: Should govt improve standard of living
* helpnot: Should govt do more or less?
* helpsick: Should govt help pay for medical care
* helpblk: Should govt aid blacks?

The investigation will try to figure out if those four variable are independent in pairs in order to 
proceed to other questions such as how education and wealth affect the opinions on governmental policies 
in 2012. Before stating the hypotheses, we will create a unified framework for these variables.

```{r data extraction}
dataset <- gss %>% select(year,helppoor,helpnot,helpsick,helpblk) %>% na.omit
levels(dataset$helppoor) <- c("Yes","Between Yes/No","No")
levels(dataset$helpnot)  <- c("Yes","Between Yes/No","No")
levels(dataset$helpsick) <- c("Yes","Between Yes/No","No")
levels(dataset$helpblk)  <- c("Yes","Between Yes/No","No")
```

We will test $\frac{4\cdot 3}{2} = 6$ $\chi^2$ hypotheses.

<u><b>Table 1</b></u>

|Hypothesis        |                                                       |
|:-----------------|:------------------------------------------------------|
|$\mathcal{H}_{0}$:|Is there denpendency between the X and Y variables?    |
|$\mathcal{H}_{A}$:|There is no dependency between the X and Y variables.  |


X and Y are paired variables from the ones we mentioned in the beginning of this section, we will also 
have to adjust the $\alpha$ level (5%) by applying the __Bonferroni__ correction 
$\alpha=\frac{0.05}{6}\approx0.00833$, since using the same dataset to test hypotheses of the same 
nature might inflate Type I error rate.

## Part 3: Exploratory data analysis

### Histograms With Respect To Time

We will search the historical trends of the opinion on the topic of governmental intervention to help 
people or not with regard to being poor,provide general help more or less, provide medical care and help 
blacks.

```{r plots,warning = FALSE,fig.align = "center"}
g <- ggplot(dataset)
g + geom_histogram(aes(x = helppoor),color = 'black',stat = 'count') + facet_wrap(. ~ year) + 
  theme(axis.text.x = element_text(angle = -90, hjust = 0)) -> g1
g + geom_histogram(aes(x = helpnot),color = 'black',stat = 'count') + facet_wrap(. ~ year) + 
  theme(axis.text.x = element_text(angle = -90, hjust = 0)) -> g2
g + geom_histogram(aes(x = helpsick),color = 'black',stat = 'count') + facet_wrap(. ~ year) + 
  theme(axis.text.x = element_text(angle = -90, hjust = 0)) -> g3
g + geom_histogram(aes(x = helpblk),color = 'black',stat = 'count') + facet_wrap(. ~ year) + 
  theme(axis.text.x = element_text(angle = -90, hjust = 0)) -> g4
gridExtra::grid.arrange(g1,g2,ncol = 2)
```

```{r plos2,warning = FALSE,fig.align = "center"}
gridExtra::grid.arrange(g3,g4,ncol = 2)
```

### Remarks

We notice that there is a same count trend between the levels of _helpoor_ and _helpnot_ with a slight 
differentiation in the first years. For the other pair of plots, we observe a positive tendency towards
helping the sick with the tax payers' money and a general tendency to not helping black people as the 
years pass by.

## Part 4: Inference

We will subset the dataset to get the measures for the year 2012.

```{r subset 2012}
dataset2012 <- dataset %>% filter(year == 2012)
```

In the following table we count all levels for all four variables and test the $\chi^2$ requirements.

```{r assign variables to level count}
helppoor <- table(dataset2012$helppoor)
helpnot  <- table(dataset2012$helpnot)
helpsick <- table(dataset2012$helpsick)
helpblk  <- table(dataset2012$helpsick)
```

<u><b>Table 2</b></u>

|1           |2          |3           |4          |
|:-----------|-----------|------------|-----------|
|helppoor    |helpnot    |helpsick    |helpblk    |
|`r helppoor`|`r helpnot`|`r helpsick`|`r helpblk`|


__3rd__ row: "Yes, Between Yes/No, No" assigned to each figure in each cell respectively.

### Conditions For $\chi^2$

We can hypothesize that the sample observations are independent and that the
sample assignment is random. The sample size falls 
way below the 10% of the overall population for the year 2012 and  from table 2 it is evident that each 
cell (level of variable) has at least 5 observations.

### Testing

Tests 1-2,1-3,1-4,2-3,2-4,3-4

```{r tests}
chisq.test(rbind(helppoor,helpnot))$p.value  -> pvalue1
chisq.test(rbind(helppoor,helpsick))$p.value -> pvalue2
chisq.test(rbind(helppoor,helpsick))$p.value -> pvalue3
chisq.test(rbind(helpnot,helpsick))$p.value  -> pvalue4
chisq.test(rbind(helpnot,helpblk))$p.value   -> pvalue5
chisq.test(rbind(helpsick,helpblk))$p.value  -> pvalue6
c(pvalue1,pvalue2,pvalue3,pvalue4,pvalue5,pvalue6) < 0.05/6
```

We would fail to reject the null hypotheses 1 and 6, meaning that there is no evidence to 
support the rejection of the null hypotheses 

$\mathcal{H}_{0}$: __helpoor__ and __helpnot__ are independent 

$\mathcal{H}_{0}$: __helpsick__ and __helpblk__ are independent

on the other hand our evindence favors the _alternative_ 
hypothesis for tests 2, 3 and 4 meaning that there exists extreme evidence (near zero p-values) that their
respective variables are __not independent__.

<script>
$( "input.hideshow" ).each( function ( index, button ) {
  button.value = 'Show Output';
  $( button ).click( function () {
    var target = this.nextSibling ? this : this.parentNode;
    target = target.nextSibling.nextSibling;
    if ( target.style.display == 'none') {
      target.style.display = '';
      this.value = 'Hide Output';
    } else {
      target.style.display = 'none';
      this.value = 'Show Output';
    }
  } );
} );

$("input.hideshow").click()
</script>