---
title: "Practice Quiz 1"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```
<style>body{text-align: justify}</style>
### 1.

```{r q1}
question("Suppose we are interested in studying how much chocolate is consumed by 
         Coursera students, measured in grams per week. After surveying 500 students, we 
         calculate an average of 175 grams per week with a standard deviation of 195 
         grams per week. Which of the following is not necessarily true?",
         answer("$\\bar{x} = 175,s = 195$"),
         answer("A point estimate for the population standard deviation is 195."),
         answer("A histogram of the samples will be skewed to the right.",
                correct = TRUE),
         answer("Just because the sample statistics are these values doesn't mean the
                population values will be exactly equal to them, therefore it's not
                necessarily true that $\\mu = 175,\\sigma = 195$."))
```

### 2.

```{r q2}
question("Which of the following is false?",
         answer("Standard error measures the variability in means of samples of the same 
         size taken from different populations.",correct = TRUE),
         answer("Standard error computed based on a sample standard deviation will always
         be lower than the standard deviation of that sample."),
         answer("As the sample size increases, the variability of the sampling 
         distribution decreases."),
         answer("In order to reduce the standard error by half, sample size should be 
         increased by a factor of 4."))
```

### 3.

```{r q3}
question("The ages of pennies at a particular bank follow a nearly normal distribution 
         with mean 10.44 years with standard deviation 9.2 years. Say you take random 
         samples of 30 pennies, find the mean age in each sample, and plot the 
         distribution of these means. Which of the following are the best estimates for 
         the center and spread of this distribution?",
         answer("mean = 10.44/30 = 0.348</br>
         standard error = $(9.2/30)^2 = 0.094$"),
         answer("mean = 10.44</br>
         standard error = 9.2/30 = 0.31"),
         answer("mean = 10.44,</br>
         standard error = 9.2"),
         answer("mean = 10.44</br>
         standard error = $\\frac{9.2}{\\sqrt{30}} = 1.689$",correct = TRUE))
```

### 4.

```{r q4}
question("Which of the following is true about sampling distributions?",
         answer("Shape of the sampling distribution is always the same shape as the 
         population distribution, no matter what the sample size is."),
         answer("Sampling distribution of the mean is always right skewed since means
         cannot be smaller than 0."),
         answer("Sampling distributions get closer to normality as the sample size 
         increases.",correct = TRUE),
         answer("Sampling distributions are always nearly normal."))
```

### 5.

```{r q5}
question("To get an estimate of consumer spending in the U.S. following the Thanksgiving 
         holiday, 436 randomly sampled American adults were surveyed. Their daily 
         spending for the six-day period following Thanksgiving averaged $84.71. A 95% 
         confidence interval based on this sample is ($80.31, $89.11). Which of the 
         following are true? </br>
         I. We are 95% confident that the average spending of the 436 American adults in 
         this sample is between $80.31 and $89.11.</br>
         II. If we collected many random samples of the same size and calculated a 
         confidence interval for daily spending for each sample, then we would expect 95%
         of the intervals to contain the true population parameter.</br>
         III. We are 95% confident that the average spending of all American adults is 
         between $80.31 and $89.11.",
         answer("I and II"),
         answer("I and III"),
         answer("II and III",correct = TRUE),
         answer("I, II, and III"),
         answer("None"))
```

### 6.

```{r q6}
question("Which of the following is false about confidence intervals?All else held 
         constant.",
         answer("as the standard deviation of the sample increases, the width
                increases."),
         answer("as the sample size increases, the margin of error decreases."),
         answer("as the confidence level increases, the width decreases.",
                correct = TRUE),
         answer("as the sample mean increases, the margin of error stays constant."))