---
title: "Quiz 1"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include = FALSE}
library(learnr)
library(gradethis)
knitr::opts_chunk$set(echo = FALSE)
gradethis_setup()
```
<style>body{text-align: justify}</style>
### 1.

<b>Researchers studying anthropometry collected body girth measurements and skeletal 
diameter measurements, as well as age, weight, height and gender, for 507 
physically active individuals. The histogram below shows the sample distribution of
heights in centimeters, and the table shows sample statistics calculated based on 
this sample. </b>

```{r fig1}
fig <- jpeg::readJPEG("fig1.jpg")
grid::grid.raster(fig)
```
```{r q1}
question("Which of the following is not necessarily true?",
         answer("The sample median is 170.3 cm."),
         answer("The population mean is 171.1 cm.",correct = TRUE),
         answer("The point estimate for the population mean is 171.1 cm."),
         answer("The sample mean is 171.1 cm."))
```

### 2.

```{r q2}
question("Which of the following is false?",
         answer("In order to reduce the standard error by half, sample size should be
                doubled.",correct = TRUE),
         answer("As the sample size increases, the variability of the sampling 
         distribution decreases."),
         answer("Standard error computed based on a sample standard deviation will always 
         be lower than the standard deviation of that sample."),
         answer("Standard error measures the variability in means of samples of the same 
         size taken from the same population."))
```

### 3.

```{r q3}
question("For the standard deviation $\\sigma$ or s and the standard error SE, which of
         the following is the correct set of descriptions?",
         answer("s: variability in sample data</br>
         SE: variability in point estimates from different samples of the same size and 
         from same population</br>
         $\\sigma$: variability in population data",correct = TRUE),
         answer("$\\sigma$: variability in sample data</br>
         s: variability in point estimates from different samples of the same size and 
         from same population</br>
         SE: variability in population data"),
         answer("$\\sigma$: variability in sample data</br>
         SE: variability in point estimates from different samples of the same size and 
         from same population</br>
         s: variability in population data"),
         answer("SE: variability in sample data</br>
         $\\sigma$: variability in population data</br>
         s: variability in point estimates from different samples of the same size and 
         from same population"))
```

### 4.
<b>Four plots are presented below. The plot at the top is a distribution for a
population. The mean is 60 and the standard deviation is 18. Also shown below is a
distribution of

(1) a single random sample of 500 values from this population,

(2) a distribution of 500 sample means from random samples of each size 18,

(3) a distribution of 500 sample means from random samples of each size 81.</b>

```{r fig2}
fig <- jpeg::readJPEG("fig2.jpg")
grid::grid.raster(fig)
```
```{r q4}
question("Determine which plot (A, B, or C) is which.",
         answer("(1) one sample, n = 500 - Plot C</br>
         (2) 500 samples, n = 18 - Plot A</br>
         (3) 500 samples, n = 81 - Plot B"),
         answer("(1) one sample, n = 500 - Plot C</br>
         (2) 500 samples, n = 18 - Plot B</br>
         (3) 500 samples, n = 81 - Plot A"),
         answer("(1) one sample, n = 500 - Plot A</br>
         (2) 500 samples, n = 18 - Plot B</br>
         (3) 500 samples, n = 81 - Plot C"),
         answer("(1) one sample, n = 500 - Plot B</br>
         (2) 500 samples, n = 18 - Plot C</br>
         (3) 500 samples, n = 81 - Plot A",correct = TRUE),
         answer("(1) one sample, n = 500 - Plot A</br>
         (2) 500 samples, n = 18 - Plot C</br>
         (3) 500 samples, n = 81 - Plot B"))
```

### 5.

```{r q5}
question("The General Social Survey (GSS) is a sociological survey used to collect data 
         on demographic characteristics and attitudes of residents of the United States. 
         In 2010, the survey collected responses from over a thousand US residents. The 
         survey is conducted face-to-face with an in-person interview of a 
         randomly-selected sample of adults. One of the questions on the survey is “For 
         how many days during the past 30 days was your mental health, which includes 
         stress, depression, and problems with emotions, not good? Based on responses 
         from 1,151 US residents, the survey reported a 95% confidence interval of 3.40 
         to 4.24 days in 2010. Given this information, which of the following statements 
         would be most appropriate to make regarding the true average number of days of 
         “not good” mental health in 2010 for US residents?",
         answer("There is not sufficient information to calculate the margin of error of 
         this confidence interval."),
         answer("For all US residents in 2010, there is a 95% probability that the true 
         average number of days of “not good” mental health is between 3.40 and 4.24 
         days."),
         answer("For all US residents in 2010, based on this 95% confidence interval, we 
         would reject a null hypothesis stating that the true average number of days of 
         “not good” mental health is 5 days.",correct = TRUE),
         answer("For these 1,151 residents in 2010, we are 95% confident that the average
         number of days of “not good” mental health is between 3.40 and 4.24 days."))
```

### 6.

```{r q6}
question("Suppose we collected a sample of size n = 100 from some population and used the
         data to calculate a 95% confidence interval for the population mean. Now suppose
         we are going to increase the sample size to n = 300. Keeping all else constant,
         which of the following would we expect to occur as a result of increasing the
         sample size? </br>
         I.   The standard error would decrease.</br>
         II.  Width of the 95% confidence interval would increase. </br>
         III. The margin of error would decrease.",
         answer("II and III"),
         answer("I and III",correct = TRUE),
         answer("I and II"),
         answer("I, II, and III"),
         answer("None"))
```

### 7.

```{r q7}
question("A company offering online speed reading courses claims that students who take 
         their courses show a 5 times (500%) increase in the number of words they can 
         read in a minute without losing comprehension. A random sample of 100 students 
         yielded an average increase of 415% with a standard deviation of 220%.</br></br>
         Calculate a 95% confidence interval for the average increase in number of words 
         students can read in a minute without losing comprehension. Choose the closest 
         answer.",
         answer("(371.88, 458.12)",correct = TRUE),
         answer("(412.09, 417.91)"),
         answer("(378.7, 451.3)"),
         answer("(411.37, 418.63)"))
```