---
title: "Practice Quiz 3"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup,include = FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```
<style>body{text-align: justify}</style>

### 1.

<b>Data were collected on 200 high schools students’ scores on various tests, 
including science, math, reading and social studies as well as the gender of the 
students. The model output for predicting science scores from the rest of the 
variables is shown below.</b>

```{r fig1}
grid::grid.raster(jpeg::readJPEG("fig1.jpg"))
```

```{r q1}
question("Which of the following is the linear model for female students?",
         answer("$\\widehat{science} = 12.325 + 0.389 math + 0.050 social studies - 1.675 reading$"),
         answer("$\\widehat{science} = 14.335 + 0.389 math + 0.050 social studies + 0.335 reading$"),
         answer("$\\widehat{science} = 12.325 + 0.389 math + 0.050 social studies + 0.335 reading$"),
         answer("$\\widehat{science} = 10.315 + 0.389 math + 0.050 social studies + 0.335 reading$",
                correct = TRUE))
```

### 2.

<b>We modeled the gas mileage of 398 cars built in the 1970’s and early 1980’s using engine displacement
(in cubic inches), year of manufacture in relation to 1970 (e.g. 4 means the car was built in 1974; 12
means built in 1982, etc.), and manufacturing site (domestic to the USA = 0; foreign to the USA = 1). The
regression output is provided below. Note that domestic is the reference level for manufacturing site.</b>

```{r fig2}
grid::grid.raster(jpeg::readJPEG("fig2.jpg"))
```

```{r q2}
question("Which of the following is the best interpretation of the slope of year?",
         answer("All else held constant, the model predicts that later model cars will get an average of 
         0.72 additional miles per gallon for each year difference in the date of manufacture.",
         correct = TRUE),
         answer("All else held constant, the model predicts that as the date of manufacture increases by 1 
         year, gas mileage changes 2.21 times as fast for foreign cars as it does for domestic cars."),
         answer("When a particular car is manufactured again in the following year, its gas mileage will 
         improve by 0.72 miles per gallon."),
         answer("All else held constant, the model predicts that later model cars will get an average of 
         12.48 additional miles per gallon for each year difference in the date of manufacture."))
```

### 3.

<b>We modeled the gas mileage of 398 cars built in the 1970’s and early 1980’s using engine displacement 
(in cubic inches), year of manufacture in relation to 1970 (e.g. 4 means the car was built in 1974; 12 
means built in 1982, etc.), and manufacturing site (domestic to the USA = 0; foreign to the USA = 1). The 
regression output is provided below. Note that domestic is the reference level for manufacturing site.</b>

```{r fig3}
grid::grid.raster(jpeg::readJPEG("fig3.jpg"))
```

```{r q3}
question("Which of the following is false?",
         answer("Given information on the manufacturing site of the car and the year of manufacture, engine
         displacement is a significant predictor of gas mileage."),
         answer("The 95% confidence interval for the slope of the displacement coefficient can be 
         calculated as −0.04±[1.96∗(−16.42)].",
         correct = TRUE),
         answer("Given the engine displacement and manufacturing site, year of manufacture is a significant
         predictor of gas mileage."),
         answer("If we add another variable to the model, for example the price of the car, the p-values 
         associated with year of manufacture, site of manufacture, and engine displacement may change."))
```

### 4.

```{r q4}
question("You are considering adding an explanatory variable to an existing multiple linear regression 
         model. Which of the following statements is generally true regarding $R^2$ and adjusted $R^2$
         as a result of adding the variable?",
         answer("If the variable is a meaningful predictor, $R^2$ will increase while adjusted $R^2$
         will stay about the same."),
         answer("If the variable is not a meaningful predictor, $R^2$ and adjusted $R^2$ will both 
         decrease."),
         answer("If the variable is not a meaningful predictor, $R^2$ will be very close to 1 and 
         adjusted $R^2$ will decrease."),
         answer("If the variable is a meaningful predictor, $R^2$ and adjusted $R^2$ will both 
         increase.",correct = TRUE),
         answer("If the variable is a meaningful predictor, adjusted $R^2$ will increase and be higher 
         than $R^2$."),
         answer("If the variable is a meaningful predictor, $R^2$ will increase while adjusted $R^2$
         will decrease and become closer to the value of $R^2$."),
         answer("If the variable is not a meaningful predictor, $R^2$ will decrease and adjusted $R^2$
         will stay about the same."))
```

### 5.

```{r q5}
question("Which of the following is true?",
         answer("A model selected using the adjusted $R^2$ backwards selection approach will only 
         contain explanatory variables that are significant at the 5% level."),
         answer("Adjusted $R^2$ may or may not be smaller than $R^2$, depending on the sample size and 
         the number of predictors in the model."),
         answer("A parsimonious model is the model containing the highest possible number of
                predictors."),
         answer("Adjusted $R^2$ applies a penalty for the number of predictors included in the regression
         model.",correct = TRUE))
```

### 6.

```{r q6}
question("Which of the following is false about conditions for multiple linear regression?",
         answer("The residuals plot should show constant variability of residuals around 0."),
         answer("It is ideal for there to be no strong relationships between any of the explanatory 
         variables."),
         answer("When the residuals are plotted in a histogram, they should appear normally distributed 
         around 0."),
         answer("With multiple predictors in the model, it’s not necessary for each of the numerical 
         explanatory variables to have a linear relationship with the response variable.",correct = TRUE))
```

### 7.

```{r q7}
question("Which of the following is false?",
         answer("In backwards model selection using adjusted $R^2$ as the criterion, we drop variables 
         from the model, one at a time, until adjusted $R^2$ is maximized."),
         answer("When dealing with collinearity, a useful strategy is to add more predictors to the model,
         one at a time, until the bad effects of collinearity disappear from the analysis.",
         correct = TRUE),
         answer("$R^2$ is always greater than or equal to adjusted $R^2$."))
```

### 8.

```{r q8}
question("True / False. If the F-test assessing the overall significance of a multiple linear regression 
         yields a significant p-value, all variables included in the model must be significant 
         predictors.",answer("TRUE"),answer("FALSE",correct = TRUE))
```
