---
title: "Quiz 3"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup,include = FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```
<style>body{text-align: justify}</style>

### 1.


<b>We modeled the gas mileage of 398 cars built in the 1970’s and early 1980’s using engine displacement (in
cubic inches), year of manufacture in relation to 1970 (e.g. 4 means the car was built in 1974; 12 means
built in 1982, etc.), and manufacturing site (domestic to the USA = 0; foreign to the USA = 1). The
regression output is provided below. Note that domestic is the reference level for manufacturing site.</b>

```{r fig4}
grid::grid.raster(jpeg::readJPEG("fig4.jpg"))
```

```{r q1}
question("Which of the following is the degrees of freedom associated with the p-value for site? ",
         answer("398"),answer("394",correct = TRUE),answer("395"),answer("3"),answer("2"))
```

### 2.

<b>We modeled the gas mileage of 398 cars built in the 1970’s and early 1980’s using engine displacement 
(in cubic inches), year of manufacture in relation to 1970 (e.g. 4 means the car was built in 1974; 12 
means built in 1982, etc.), and manufacturing site (domestic to the USA = 0; foreign to the USA = 1). The
regression output is provided below. Note that domestic is the reference level for manufacturing site.</b>

```{r fig5}
grid::grid.raster(jpeg::readJPEG("fig5.jpg"))
```


```{r q2}
question("Which of the following is the correct predicted gas mileage (in miles per gallon) for a domestic 
         car with an engine displacement of 350 cubic inches built in 1975?",
         answer("−0.04×350+0.72×1975"),
         answer("26.86−0.04×350+0.72×1975+2.21"),
         answer("26.86−0.04×350+0.72×5",correct = TRUE),
         answer("−0.04×350+0.72×5+2.21"))
```

### 3.

<b>Body fat percentage can be complicated to estimate, while variables such as Age, Height, Weight, and
measurements of various body parts are easy to measure. Based on data1 on body fat percentage and other
various measurements, a linear regression model was developed to predict body fat percentage, based on easy
to obtain measurements. The model output is shown below.</b>

```{r fig6}
grid::grid.raster(jpeg::readJPEG("fig6.jpg"))
```

```{r q3}
question("Based on this output, what is the correct interpretation of the coefficient for wrist?",
         answer("For every 1 inch decrease in wrist circumference, we’d expect a decrease in body fat 
         percentage of about (13.57+1.14)%, on average."),
         answer("For every 1 inch decrease in wrist circumference, we’d expect a decrease in body fat 
         percentage of 1.14%, on average."),
         answer("For every 1 inch increase in wrist circumference, we would expect body fat percentage to
         be lower by 1.14%, on average.",correct = TRUE),
         answer("For every 1 inch increase in wrist circumference, we’d expect a decrease in body fat 
         percentage of about 1.14% plus or minus 1.96∗0.47%, on average."))
```

### 4.

<b>A random sample of 200 women who were at least 21 years old, of Pima Indian heritage and living near
Phoenix, Arizona, were tested for diabetes according to World Health Organi- zation criteria. The model
below is used for predicting their plasma glucose concentration based on their diastolic blood pressure
(bp, in mmHg), age (age, in years), and whether or not they are diabetic (type, Yes and No). </b>

```{r fig7}
grid::grid.raster(jpeg::readJPEG("fig7.jpg"))
```

```{r q4}
question("Which of the following is false?",
         answer("The model as a whole is significant, even though one of the variables (blood pressure) 
         may not be."),
         answer("The predicted difference in blood glucose levels of two 25 year old females who don’t 
         have diabetes one of whom has a blood pressure of 70mmHg and the other 75 mmHG is 0.35∗5=1.75"),
         answer("The model predicts that women without diabetes have blood glucose levels that are on 
         average 26.57 higher than those who have diabetes, given that they are similar in terms 
         of their blood pressure and age.",correct = TRUE),
         answer("The model explains 28% of variability in blood glucose levels of these women."))
```

### 5.

<b>Researchers investigating academic performance of high school students examined data from 2011 from all
50 states and DC (n=51). The data included information on

* SAT math (response variable) - average SAT math score of all students in the state who took the exam

* per_ppl_sp - average number of dollars per pupil spent on education by the state

* perc_take - percentage of high school seniors in the state that took the exam

The output of the model fit by one of the researchers is shown below: </b>

```{r fig8}
grid::grid.raster(jpeg::readJPEG("fig8.jpg"))
```

```{r q5}
question("What proportion of the variability in the response variable is explained by the model? Choose 
         the closest answer.",
         answer("8%"),answer("6%"),answer("31%"),answer("74%",correct = TRUE))
```

### 6.

<b>Consider the following output from a multiple linear regression model with 10 predictors.</b>

```{r fig9}
grid::grid.raster(jpeg::readJPEG("fig9.jpg"))
```

```{r q6}
question("If you were doing backwards selection on this model using p-value as the criterion, which of the
         following would be an acceptable next step?",
         answer("Remove the variable “dollar” because it has the highest p-value.",
                correct = TRUE),
         answer("Remove any one of the variables with a high p-value which as long as removing the 
         variable does not cause the adjusted $R^2$ to decrease in the re-fitted model."),
         answer("Remove the variables “password” and “dollar” because their high p-values indicate 
         collinearity with other variables."),
         answer("Remove one of the variables “ re subj” or “ attach” because they both have the lowest 
         p-values."))
```

### 7.

```{r q7}
question("Which of the following is false about conditions for multiple linear regression?",
         answer("Explanatory variables should have strong relationships with each other.",correct = TRUE),
         answer("Explanatory variables should have linear relationship with the response variable."),
         answer("Residuals should have constant variance."),
         answer("Residuals should be normally distributed around 0."))
```

### 8.

```{r q8}
question("Which of the following is the best definition of a parsimonious model?",
         answer("The model with the highest $R^2$"),
         answer("The model with the most number of predictors."),
         answer("The model that includes all the predictors that your audience is interested in."),
         answer("The simplest model with the highest predictive power.",correct = TRUE))
```

### 9.

```{r q9}
question("A high correlation between two explanatory variables such that the two variables contribute 
         redundant information to the model is known as",
         answer("homogeneity"),
         answer("adjusted R^2"),
         answer("multiple correlation"),
         answer("heteroscedasticity"),
         answer("multiple interaction"),
         answer("homoscedasticity"),answer("heterogeneity"),
         answer("collinearity",correct = TRUE))
```

### 10.

```{r q10}
question("Suppose you have performed forward selection using adjusted $R^2$ as the criterion and have
         chosen a model with 6 predictors. Based on your studies of model selection, which of the
         following is most likely to be true?",
         answer("The model you’ve arrived at is the most parsimonious model."),
         answer("All 6 predictors will be significant in the model."),
         answer("If any of your 6 predictors is not significant in the model, given the other 
         predictors, then your slope coefficients will be biased."),
         answer("Your final model has a higher adjusted $R^2$ than any of the smaller models
         you tried.",correct = TRUE))
```