---
title: "Quiz 3"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

<style>body{text-align: justify}</style>

### 1.

```{r q1}
question("Which of the following is false about bootstrapping?",
         answer("A bootstrap confidence interval constructed based on a biased sample will still yield 
                an unbiased estimate for the population parameter of interest.",correct = TRUE),
         answer("Bootstrap distributions that are extremely skewed or have isolated clumps of values may
         yield unreliable confidence intervals."),
         answer("Bootstrap distributions are constructed by sampling with replacement from the original 
         sample, while sampling distributions are constructed by sampling with replacement from the 
         population."),
         answer("The endpoints of a 95% bootstrap confidence interval are the cutoff values for the top 
         and bottom 2.5% of the bootstrap distribution."))
```

### 2.

```{r q2}
question("Suppose we wanted to compare the rates of return for two stocks: the technology company Intel 
         and the U.S. airline Southwest Airlines. To compare the rates of return, we take a random 
         sample of 50 days of Intel's stock returns and another random sample of 50 days for Southwest's
         stock returns (not necessarily the same days). These data should not be treated as paired. Why 
         would these data not be considered paired data?",
         answer("50 observations is not enough to be able to consider the data as paired."),
         answer("When random sampling is involved, data can't be treated as paired."),
         answer("The data can't be considered paired data because the two companies are in different
                industries.",),
         answer("The data can't be considered paired data because the days for which we have Intel data 
                may be different from the days for which we have Southwest Airlines data.",
                correct = TRUE))
```

### 3.

```{r q3}
question("Which of the following is false about bootstrap and sampling distributions?",
         answer("Both distributions are comprised of sample statistics."),
         answer("Both distributions get narrower as the standard deviation decreases."),
         answer("Bootstrap distributions are centered at the sample statistic, sampling distributions are centered
         at the population parameter."),
         answer("Both distributions are created by sampling with replacement from the population.",correct = TRUE))
```

### 4.

<b>Researchers studying IQ scores of mothers and fathers of "gifted" children collected data from 36 gifted
children and their parents. First, differences in IQ scores of the father and the mother were calculated for each
child (calculated as father's IQ score - mother's IQ score). The dot plot below shows the bootstrap distribution of
means of 200 bootstrap samples taken from this original sample of differences in IQ scores. The mean of the
bootstrap distribution is approximately -3.48 points and the bootstrap standard error is 1.3 points. Assume the
usual conditions for constructing a bootstrap confidence interval are satisfied. </b>

```{r q4}
grid::grid.raster(jpeg::readJPEG('fig3.jpg'))
question("Which of the following statements is false?",
         answer("A 95% bootstrap confidence interval for the difference in IQ scores is approximately 
                (-6, -0.9)."),
         answer("Since 0 is apparently an unusual value for the statistic, then at the 5% significance
         level we would fail to reject a null hypothesis of that claims that the fathers' and mothers' 
         average IQs are equal.",correct = TRUE),
         answer("It's likely that in the original sample, most mothers had higher IQ scores than the 
                fathers."),
         answer("A 90% bootstrap confidence interval for the difference in IQ scores would is 
         approximately (-5.6, -1.3).)"))
```

### 5.

```{r q5}
question("An insurance company wants to estimate (using a confidence interval) its average claim amount using data 
         from 20 randomly selected claims. Which of the following is false?",
         answer("A confidence interval based on this sample is not accurate since the sample size is 
                small.",correct = TRUE),
         answer("The confidence interval can also be calculated using bootstrapping."),
         answer("The critical t-score, $t^{*}$ has 19 degrees of freedom."),
         answer("If the distribution of the sampled claim amounts is not extremely skewed, a T interval is
         appropriate."))
```

### 6.

<b>The figure below shows three t-distribution curves.</b>

```{r q6}
grid::grid.raster(jpeg::readJPEG("fig4.jpg"))
question(" Which curve has the highest degree of freedom?",
         answer("dashed"),answer("solid",correct = TRUE),answer("dotted"))
```

### 7.

```{r q7}
question("My friend, Tom, believes that his supermarket's prices are lower than mine, and sets an 
         alternative hypothesis test reflecting this. We construct a list of 10 identical items and 
         purchase them at our respective stores. Tom wants to know if these data support his hypothesis.
         Which of the following is the correct description of Tom's situation?",
         answer("Tom has a two-sided alternative hypothesis and should do a paired t-test."),
         answer("Tom has a one-sided alternative hypothesis and should do an independent samples 
                t-test."),
         answer("Tom has a two-sided alternative hypothesis and should do an independent samples 
                t-test."),
         answer("Tom has a one-sided alternative hypothesis and should do a paired t-test.",
                correct = TRUE))
```

### 8.

```{r q8}
question("Suppose that a one-tail t test is being applied to find out if the population mean is less 
         than 100. The level of significance is 0.05 and 25 observations were sampled. The null 
         hypothesis would be rejected for t scores in which of the following regions? Choose the best 
         answer.",
         answer("T > 1.71"),
         answer("T < 1.96"),
         answer("T < −1.71",correct = TRUE),
         answer("T < −1.32"),
         answer("T > 1.32"))
```

> qt(.05,24)

### 9.

```{r q9}
question("We would like to test if students who are in the social sciences, natural sciences, arts & 
         humanities, and other fields spend the same amount of time studying for this course. What type
         of test should we use?",
         answer("F-test (ANOVA)",correct = TRUE),
         answer("z-test"),
         answer("t-test for two independent groups"),
         answer("t-test for two dependent groups"))
```

### 10.

```{r q10}
question("Which of the following is most useful for checking the equal variance across groups
         condition for ANOVA?",
         answer("Summary statistics suggesting roughly equal ranges for each group."),
         answer("Summary statistics suggesting that the means of each group are roughly equal."),
         answer("Histograms suggesting nearly normal distributions of data in each group."),
         answer("Side-by-side box plots showing roughly equally sized boxes for each group.",
                correct = TRUE))
```

### 11.

<b>Based on the ANOVA output below, what is the value of the F-statistic?</b>

```{r q11}
grid::grid.raster(jpeg::readJPEG("fig5.jpg"))
question("Choose the best answer.",answer("0.54"),answer("10.71"),answer("27.00"),
         answer("1.87",correct = TRUE),
         answer("14.45"))
```

> 75.00/40.13

### 12.

```{r q12}
question("A study compared five different methods for teaching descriptive statistics. The five methods 
         were traditional lecture and discussion, programmed textbook instruction, programmed text with 
         lectures computer instruction, and computer instruction with lectures. 45 students were 
         randomly assigned, 9 to each method. After completing the course, students took a 1-hour exam.
         We are interested in finding out if the average test scores are different for the different 
         teaching methods. The p-value of the test is 0.0168. What is the conclusion of the test?",
         answer("At most two group means are significantly different from each other."),
         answer("All five group means are significantly different from each other."),
         answer("All five group means are equal to each other."),
         answer("Only two group means are significantly different from each other."),
         answer("At least two group means are significantly different from each other.",correct = TRUE))
```

### 13.

```{r q13}
question("Researchers studying people’s sense of smell devised a measure of smelling ability. A higher 
         score on this scale means the subject can smell better. A random sample of 36 people (18 male 
         and 18 female) were involved in the study. The average score for the males was 10 with a 
         standard deviation of 3.4 and the average score for the females was 11 with a standard 
         deviation of 2.7. Which of the following is the
         correct standard error for the test evaluating whether the males and females have differing 
         smelling abilities, on average? Choose the closest answer.",
         answer("1.023",correct = TRUE),
         answer("3.504"),
         answer("1.047"),
         answer("0.801"),
         answer("0.724"))
```

> sqrt(3.4^ 2/ 18+2.7^2/ 18)

### 14.

```{r q14}
question("A study compared five different methods for teaching descriptive statistics. The five methods were
         traditional lecture and discussion, programmed textbook instruction, programmed text with lectures
         computer instruction, and computer instruction with lectures. 45 students were randomly assigned, 9 to
         each method. After completing the course, students took a 1-hour exam. We are interested in finding out if
         the average test scores are different for the different teaching methods.</br></br>
         How many pairwise tests would we need to do in order to compare all pairs of means to each other?",
         answer("3"),answer("5"),answer("10",correct = TRUE),answer("4"),answer("20"))
```

> k(k-1)/2