---
title: "Modeling and prediction for movies"
author:
  - George Papadopoulos
  - pgeorgios8@gmail.com
date:
  - "`r lubridate::today()`"
output: 
  html_document: 
    css: style.css
    fig_height: 4
    highlight: pygments
    theme: spacelab
    toc: true
---
<style>body{text-align: justify}</style>
# Section A: Aim & Data

## Setup

Big corporations were always very interested in investing in new technologies combined with 
statistical methods in order to be able to make predictions and recognize customer preferences
along with new trends! In this report we are placed head of a group of a data scientist team hired by 
_Paramount_, with the task of creating a simple and robust prediction model for 
__audience  score__ for later movies (after 2016).

Our  supervisor in this project is interested in learning what attributes make a movie popular, 
learning something new about movies and wants from our team to figure it all out. As part of this
project we will complete exploratory data analysis (EDA), modeling and prediction. We will try to 
find the simplest and more robust model to make predictions and test a prediction by extrapolating to new data.

### Load packages

The version of R used and the packages we will use in this report are the following.

```{r load-packages,message = FALSE,comment = '',warning = FALSE}
library(ggplot2)
library(dplyr)
library(statsr)
library(olsrr)
library(GGally)
library(gridExtra)
library(grid)
getRversion()
```

### Preparation

We will load the data.

```{r load-data}
load("movies.Rdata")
```

## Part 1: Data

### Overview Of Data: <u>__Data Summary And Variables__</u> {.tabset}

#### Names {.tabset}

```{r names,comment = ''}
names(movies)
```

#### Dimension {.tabset}

```{r dimension,comment = ''}
dim(movies)
```

#### Summary {.tabset}

```{r summary,comment = ''}
summary(movies)
```

#### Class Of Each Variable

```{r class-column,comment = ''}
sapply(movies,class)
```

### Information Contained In Data

The dataset contains information about movies in [Rotten Tomatoes](www.rottentomatoes.com/) 
and [IMDB](www.imdb.com). There are 651 _randomly_ sampled movies produced and released before 2016. 
There are 32 available variables, which are described in more detail in the following list.

<input type=button class=hideshow>
```{r codebook,eval = F}
Codebook

1.  title: Title of movie
2.  title_type: Type of movie (Documentary, Feature Film, TV Movie)
3.  genre: Genre of movie (Action & Adventure, Comedy, Documentary, Drama, Horror, Mystery & Suspense, Other)
4.  runtime: Runtime of movie (in minutes)
5.  mpaa_rating: MPAA rating of the movie (G, PG, PG-13, R, Unrated)
6.  studio: Studio that produced the movie
7.  thtr_rel_year: Year the movie is released in theaters
8.  thtr_rel_month: Month the movie is released in theaters
9.  thtr_rel_day: Day of the month the movie is released in theaters
10. dvd_rel_year: Year the movie is released on DVD
11. dvd_rel_month: Month the movie is released on DVD
12. dvd_rel_day: Day of the month the movie is released on DVD
13. imdb_rating: Rating on IMDB
14. imdb_num_votes: Number of votes on IMDB
15. critics_rating: Categorical variable for critics rating on Rotten Tomatoes (Certified Fresh, Fresh, Rotten)
16. critics_score: Critics score on Rotten Tomatoes
17. audience_rating: Categorical variable for audience rating on Rotten Tomatoes (Spilled, Upright)
18. audience_score: Audience score on Rotten Tomatoes
19. best_pic_nom: Whether or not the movie was nominated for a best picture Oscar (no, yes)
20. best_pic_win: Whether or not the movie won a best picture Oscar (no, yes)
21. best_actor_win: Whether or not one of the main actors in the movie ever won an Oscar (no, yes) – note that 
this is not necessarily whether the actor won an Oscar for their role in the given movie
22. best_actress win: Whether or not one of the main actresses in the movie ever won an Oscar (no, yes) – not 
that this is not necessarily whether the actresses won an Oscar for their role in the given movie
23. best_dir_win: Whether or not the director of the movie ever won an Oscar (no, yes) – not that this is not 
necessarily whether the director won an Oscar for the given movie
24. top200_box: Whether or not the movie is in the Top 200 Box Office list on BoxOfficeMojo (no, yes)
25. director: Director of the movie
26. actor1: First main actor/actress in the abridged cast of the movie
27. actor2: Second main actor/actress in the abridged cast of the movie
28. actor3: Third main actor/actress in the abridged cast of the movie
29. actor4: Fourth main actor/actress in the abridged cast of the movie
30. actor5: Fifth main actor/actress in the abridged cast of the movie
31. imdb_url: Link to IMDB page for the movie
32. rt_url: Link to Rotten Tomatoes page for the movie
```
</input>

We will also have to keep only the complete cases in order to be more precise in the next parts.

```{r data clean,warning = FALSE,comment = ''}
data <- movies %>% na.omit()
sum(is.na(data)) # check
```

## Part 2: Research question

The research question we will investigate is the following:

<b>which is the best set of predictors that can predict the audience score in the rotten tomatoes 
website based in the data set we loaded and how accurate is the extrapolation of this model to 
movies not belonging to data set, meaning movies released after 2016.</b>

In the next chunk we will present the variables we will use for building our model in the next parts.

```{r variables,comment = ''}
cols <- c(3,4,5,13,14,15,16,17,18,19,20,21,22,23,24)
data <- movies[cols] %>% na.omit() 
names(data)
```

We excluded variables which had to do with the title of the movies, studios in which the movies were directed, 
the release time (dvd/cinema), names of actors and directors and finally the urls, since these cannot be used 
for prediction.

# Section B: Building the model

## Part 3: Exploratory data analysis Part I

The response variable is "audience_score" (the score provided by the audience in rotten tomatoes), 
we will explore firstly the correlation plot between the numeric variables.

```{r corplot,fig.align = 'center'}
ggcorr(data)
```

We actually observe that there is high positive correlation between the audience score and the critics score and 
even higher positive correlation between audience score and imdb ratings, this is good since logically we 
see that the scores from different sources seem to follow the same trend.  We will continue with the other 
factor variables.

```{r boxplots,fig.align = 'center'}
g  <- ggplot(data) + theme(axis.text.x = element_text(angle = -90, hjust = 0)) 
g1 <- g + geom_boxplot(aes(x = genre,y = audience_score)) 
g2 <- g + geom_boxplot(aes(x = mpaa_rating,y = audience_score))
g3 <- g + geom_boxplot(aes(x = critics_rating,y = audience_score))
grid.arrange(g1,g2,g3,ncol = 3,top = textGrob("Audience Score Vs Factor Variables"))
```

We observe high fluctuation of the medians of audience scores between genre and critics rating which is a sign of
potential informative predictors, since the diversification can lead to more accurate predictions, In the middle 
plot though we see medians fluctuating in a specific range which might imply a bad predictor. The other variables
are __binary__ and of no interest in this section. 

## Part 4: Modeling 

Our interest is creating a robust simple model which can extrapolate beyond the data provided to our team. We 
will fit a model with all the variables and with _backwards_ propagation using the $R^2$.adjusted metric we will 
choose the best model which fits our purpose of predictions. Using the p-values might overfit the model which is 
not good for our case, since we adjust the model too much in the original data. The following commands first fit
a one-against-all linear regression model and by subtracting one variable at a time it provides the best model 
with the highest $R^2$.adjust value.

```{r model lm}
model <- lm(audience_score ~ .,data = data)
ols_step_backward_p(model) -> best_model
```

The information printed after the operation provides the list of the variables excluded by the algorithm.

```{r model lm2,comment = ''}
summary(best_model$model)
```

From the F-statistic we deduce that the model is _statistically significant_ and that not all p-values of the 
predictors fall under the 0.05 threshold, nonetheless as noted from the beginning our main goal is _prediction_
, so this is the best model that the backwards propagation algorithm yielded using the $R^2$.adjusted metric. 
Hopefully we observe that the model justifies our exploratory findings.

### Exploratory Model Analysis Part II

We will test for _independency_ between the explanatory variables and the response variable.

```{r residuals/resp,fig.align = 'center'}
par(mfrow = c(1,2),oma = c(0, 0, 2, 0))
plot(x = data$imdb_rating,y = best_model$model$residuals,col = data$audience_rating,pch = 19,
     ylab = 'residual',xlab = 'imdb rating')
abline(v = 6.5)
abline(h = 0)
plot(y = best_model$model$residuals,x = data$runtime,col = data$audience_rating,pch = 19,
     ylab = 'residual',xlab = 'runtime')
abline(h = 0)
mtext(text = "Model Residuals vs Numeric Parameters",outer = TRUE)
```

In the first plot a confounding factor is the audience rating (binary) which differentiates the two clusters, 
nontheless the scatter around the horizontal line h = 0 seems random despite some outliers.

The next step is to check for __residual normality__ and __constant variability__ of the residuals,

```{r residual/norm,fig.align = 'center'}
par(mfrow = c(1,2),oma = c(0, 0, 2, 0))
qqnorm(best_model$model$residuals,col = rgb(0,.2,.4,.4))
qqline(best_model$model$residuals,lty = 2,col = 'red')
plot(density(best_model$model$residuals),lwd = 2,col = 'green',main = 'residual density')
mtext(text = "Residuals Normality Check",outer = TRUE)
```

from the plots above the normality check is passed. Now for the __homoscedacity__ check,

```{r res vs fitted,fig.align = 'center'}
plot(best_model$model$fitted.values,best_model$model$residuals,pch = 19,
     xlab = 'fitted values',ylab = 'residuals',col = movies$audience_rating)
abline(h = 0)
```

We observe again the confounding factor which we noted before and that the spread around the line 
h = 0 shows a constant variability despite the "gap" between the two clusters. Finally we will plot the residuals
by index to explore if they are __independent__,

```{r res independency,fig.align = 'center'}
plot(best_model$model$residuals,col = 'red',pch = 19,ylab = 'residuals')
```

since we don't notice any pattern we move to the next part to use our model for _extrapolation_.

## Part 5: Prediction

<b><u>Apply For Extrapolation:</u></b>

The movie released after 2016 for which we will make a prediction with our liner model is 
[Alien Covenant (2017)](https://www.rottentomatoes.com/m/alien_covenant). The information
in the next chunk is taken by the movie link provided in the previous sentence.

```{r prediction/extrapolation,comment = ''}
data.frame(genre = "Science Fiction & Fantasy",
           runtime = 124,imdb_rating = 6.4,critics_score = 6.3,audience_rating = "Spilled"
           ,best_pic_nom = "yes",best_actress_win = "no") -> pred
predict(best_model$model,pred, interval = "prediction", level = 0.95)
```

We observe a slightly lower value of our prediction than the real audience score 55% as of 
1/20/2021! The rounded under evaluation error is `r round(predict(best_model$model,pred) - 55,2)` and we are 
95% confident that the interval (37.72772,6686361) contains the true parameter of interest, which is already 
known in our case with the value 55% and that makes our model's prediction robust per se.

## Part 6: Conclusion

Our model was created using back propagation by choosing the parameters that maximize $R^2$.adjust, we used this 
metric because we aimed at extrapolation beyond the data time scope and tried to capture the parameters
that __mostly__ affect film preferences by the audiences in the rotten tomatoes web site. We didn't conduct a 
causal analysis since we didn't randomize or blocked for a confounding factor we spotted in the plots presented,
our only goal was to create a prediction model based on _observational_ study. Ending our report, we would like 
to point out that further study on data collection variables should be conducted, for example we might need 
information on how the audience scoring is affected by a successful prequel of the movie rated or even add a 
variable which _scales_ how famous the cast is in order to free our model from actor names, finally we might want
to ensure that there is no bias in the scoring process by making the ip filtering more strict.

<script>
$( "input.hideshow" ).each( function ( index, button ) {
  button.value = 'Show Output';
  $( button ).click( function () {
    var target = this.nextSibling ? this : this.parentNode;
    target = target.nextSibling.nextSibling;
    if ( target.style.display == 'none') {
      target.style.display = '';
      this.value = 'Hide Output';
    } else {
      target.style.display = 'none';
      this.value = 'Show Output';
    }
  } );
} );

$("input.hideshow").click()
</script>