---
title: "Practice Quiz 1"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup,include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```
<style>body{text-align: justify}</style>
  

### 1.

```{r q1}
question("A statistics instructor wants to use the number of hours studied to predict exam scores in her 
         class. She wants to use a linear regression model. Data from previous years shows that the correlation 
         between these two variables is 0.76. Which of the following is the best response for whether or not the 
         instructor should use linear regression to predict exam scores for a student who studied 10 hours for the 
         final?",
         answer("Yes, because linear regression is the statistical method used to make predictions when you have 
         bivariate quantitative data."),
         answer("Linear regression could be appropriate if the scatterplot shows a clear linear relationship.",
                correct = TRUE),
         answer("No, because there is no way to prove that more hours of study causes higher exam scores."),
         answer("Yes, there is a high correlation, so it is appropriate to use linear regression."))
```

### 2.

```{r q2}
question("Which of the following is false?",
        answer("If the correlation coefficient is 1, then the slope must be 1 as well.",correct = TRUE),
        answer("The magnitude of the correlation coefficient measures the strength of the linear association between 
        two numerical variables."),
        answer("Two numerical variables with a correlation of 0.01 have very weak linear association."),
        answer("Correlation coefficient and the slope always have the same sign (positive or negative)."))
```

### 3.

<b>Sixteen student volunteers at Ohio State University drank a randomly 
assigned number of beers. Thirty minutes later, a police officer 
measured their blood alcohol content (BAC) in grams of alcohol per 
deciliter of blood. The scatterplot displays the relationship between 
BAC and number of beers consumed. If the student who drank the highest 
number of beers (9 beers) actually had a BAC of 0.15 grams/deciliter.

```{r fig}
grid::grid.raster(jpeg::readJPEG('fig1.jpg'))
```

```{r q3}
question("how would the strength of the association change?",
         answer("Stay the same"),answer("Cannot tell"),answer("Decrease"),
         answer("Increase",correct = TRUE))
```

### 4.

```{r q4}
question("The $R^2$ for the linear regression of two variables x and y is 0.60. The variables are negatively 
         associated. Which of the following is the correct correlation coefficient? Choose the closest answer.",
         answer("-0.77",correct = TRUE),
         answer("0.40"),answer("0.36"),answer("-0.36"),answer("0.77"))
```