---
title: "Quiz 1"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup,include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE,comment = '')
```
<style>body{text-align: justify}</style>

### 1.
<b>Of the four plots shown below,</b>

```{r fig2}
grid::grid.raster(jpeg::readJPEG('fig2.jpg'))
```
```{r q1}
question("which one appears to show the weakest relationship between two 
        variables?",answer("I"),answer("II"),answer("III"),answer("IV",correct = TRUE))
```

### 2.

<b>The first plot below was created by plotting data collected on two variables. Then, the second plot was
created using the same data but with different units for the dependent variable. 

```{r fig3}
grid::grid.raster(jpeg::readJPEG('fig3.jpg'))
```

```{r q2}
question("In the context of linear regression, which of the following best describes the differences 
         between the two plots?",
         answer("The correlation coefficient for the second plot has a larger absolute value, but the
                slopes of the linear relationships in the two plots are the same."),
         answer("The slope of the linear relationship in the first plot has a smaller absolute value, but 
         the correlation coefficients for the two plots are the same."),
         answer("The slope of the linear relationship in the first plot has a larger absolute value, but 
         the correlation coefficients for the two plots are the same.",correct = TRUE),
         answer("Both the slopes and the regression coefficients are the same for the two plots."),
         answer("The correlation coefficient for the second plot has a smaller absolute value, but the slopes
         of the linear relationships in the two plots are the same."))
```

### 3.

```{r q3}
question("Fill in the blank: Residuals of linear models should be distributed nearly normally around __________.",
         answer("the mean of x"),
         answer("the mean of y"),
         answer("the mean of $\\hat{y}$ (the predicted values)"),
         answer("0",correct = TRUE))
```

### 4.

<b>Sixteen student volunteers at Ohio State University drank a randomly assigned number beers. Thirty minutes later, 
a police officer measured their blood alcohol content (BAC) in grams of alcohol per deciliter of blood. The 
scatterplot displays the relationship between BAC and number of beers consumed. Suppose a mistake was found in the 
data: the student who supposedly drank the highest number of beers (9 beers) actually only drank 6. His BAC was 
recorded correctly.</b>

```{r fig4}
grid::grid.raster(jpeg::readJPEG('fig4.jpg'))
```

```{r q4}
question("In a new scatterplot, how would the strength of the association appear - compared to the strength of the 
         association shown here?",
         answer("Roughly the same as the strength of the association shown in the above scatterplot."),
         answer("Weaker than the strength of the association shown in the above scatterplot.",correct = TRUE),
         answer("Stronger than the strength of the association shown in the above scatterplot."),
         answer("It’s impossible to tell."))
```

### 5.

```{r q5}
question("The correlation between height and weight for a certain breed of plant is found to be 0.75. What percentage
         of the variability in plant weight is <b>not</b> explained by height?",
         answer("$(0.75)^2 = 0.5625$ or 56.25%"),
         answer("1−0.75 = 0.25 or 25%"),
         answer("$(1 − 0.75)^2 = 0.0625$ or 6.25%$"),
         answer("$1 − (0.75)^2 = 0.4375$ or 43.75%$",correct = TRUE))
```

### 6.

A colleague needs some help with a statistics problem: He brings you the plot shown below, along with a correlation
coefficient of 0.03 which he calculated himself. The plot shows two numerical variables which are obviously strongly
related, and as a result your colleague is afraid he made a mistake calculating the correlation coefficient: that is,
he was surprised to get an answer so close to 0.

```{r fig5}
grid::grid.raster(jpeg::readJPEG('fig5.jpg'))
```

```{r q6}
question("Given only this information, which of the following responses is the best to give your colleague?",
         answer("Your colleague must have made a mistake in his calculations. A much higher correlation coefficient
         is expected for variables that show a clear association."),
         answer("The correlation coefficient measures the strength of the linear relationship, therefore two 
         variables that have a strong non-linear association might still have a low correlation coefficient.",
         correct = TRUE))
```

### 7.

<b>The  linear model below is used for predicting poverty rate from high school graduation rate in the 51 states in 
the US (including DC).</b>

<center>
$\displaystyle\widehat{\text{poverty}} = 64.68 - 0.62\cdot\text{HS grad rate}$
</center>

<b>A snippet of the data matrix is provided below, pay attention to the scale of the data in solving this question.
</b>

```{r fig6}
grid::grid.raster(jpeg::readJPEG('fig6.jpg'))
```
```{r q7}
question("High school graduation rate for North Carolina is 81.4% and the poverty rate is 13.1%. What is the residual
         for this observation? Choose the closest answer.",
         answer("-1.1",correct = TRUE),answer("24.8"),answer("-24.8"),answer("0"),answer("1.1"))
```

```{r q7b,exercise = TRUE}
## Computations here

```

### 8.

<b>The following ANOVA output is for the linear model predicting nicotine content (in mg) from tar content (in mg).
</b>

```{r fig7}
grid::grid.raster(jpeg::readJPEG('fig7.jpg'))
```

```{r q8}
question("Which of the following is $R^2$? Choose the closest answer.",
         answer("20%"),answer("5%"),answer("0.2%"),answer("95%",correct = TRUE),answer("4%"))
```

```{r q8b,exercise = TRUE}
## Computations here

```

### 9.

<b>Based on an observational study, a clinical psychologist finds that 
the relationship between the number of weeks spent in a therapy hospital
and number of seizures per week is described by the following equation:</b>

<center>
$\displaystyle\widehat{\text{seizures}} = 14.09 - 0.91\cdot\text{weeks}$
</center>

```{r q9}
question("Which of the following is the best interpretation of the slope estimate?",
         answer("Each additional week spent in a therapy hospital decreases the number of seizures
                per week by 0.91."),
         answer("All patients start their treatment with at least 14.09 seizures per week."),
         answer("For each additional seizure per week, we would expect the average number of additional weeks spent 
         in the therapy hospital to be higher by 0.91 seizures."),
         answer("For each additional week spent in the therapy hospital, we would expect the average number of 
         seizures per week to lower by 0.91 seizures.",correct = TRUE))
```