---
title: "Practice Quiz 2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup,include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```
<style>body{text-align: justify}</style>

### 1.

```{r q1}
question("Does meditation cure insomnia? Researchers randomly divided 400 people into two equal-sized 
         groups. One group meditated daily for 30 minutes, the other group attended a 2-hour 
         information session on insomnia.</br>
         At the beginning of the study, the average difference between the number of minutes slept between 
         the two groups was about 0. After the study, the average difference was about 32 minutes, and 
         the meditation group had a higher average number of minutes slept.</br>
         To test whether an average difference of 32 minutes could be attributed to chance, a statistics 
         student decided to conduct a randomization test. She wrote the number of minutes slept by each 
         subject in the study on an index card. She shuffled the cards together very well, and then dealt 
         them into two equal-sized groups, representing those who meditated and those who attended the
         information session.</br>
         Which of the following best describes the outcome of the randomization test.",
         answer("If meditation is effective, the average difference between the values on the two stacks of cards is 
         expected to be more than 32 minutes."),
         answer("The average difference between the two values on the two stacks of cards is expected to be about 
         32 minutes."),
         answer("The average difference between the two values on the two stacks of cards is expected to be about 0
                minutes.",correct = TRUE))
```

### 2.

<b>Tipping at a restaurant. The owner of a restaurant interested in studying the tipping patterns of his customers
collected restaurant bills over a two week period that he believes provides a representative sample of his customers.
The data recorded from 157157157 bills include the amount of the bill (in \$) and the size of the tip (in \$). The 
correlation coefficient of the relationship between these two variables is 0.915.</b>

```{r fig1}
grid::grid.raster(jpeg::readJPEG("fig1.jpg"))
```

```{r q2}
question("The regression model and a scatterplot of these data are shown below. Which of the following is false?",
         answer("The regression model will yield a more reliable prediction for the size of the tip when the bill 
         amount is $20 versus when the bill amount is $70."),
         answer("The amount of the bills explains roughly 84% of the variability in the sizes of the tips."),
         answer("The intercept serves only to adjust the height of the regression line."),
         answer("A 95% confidence interval for the slope can be calculated as 0.18±(28.25×0.01)",correct = TRUE),
         answer("For each additional dollar spent the tip is expected to be higher on average by $0.18 (18
                cents)."))
```

### 3.

```{r q3}
question("True / False: Not all leverage points are influential.",answer("TRUE",correct = TRUE),answer("FALSE"))
```