---
title: "Quiz 2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup,include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```
<style>body{text-align: justify}</style>

### 1.

<b>The scatterplot on the right shows the relationship between percentage of white residents and percentage 
of households with a female head in all 50 US States and the District of Columbia (DC).</b>

```{r fig2}
grid::grid.raster(jpeg::readJPEG("fig2.jpg"))
```
```{r q1}
question("Which of the below best describes the two points marked as DC and Hawaii?",
         answer("DC and Hawaii should both be excluded from a simple linear regression analysis."),
         answer("Hawaii is not an outlier, and DC is not a leverage point."),
         answer("Neither DC nor Hawaii appear to be leverage points."),
         answer("Hawaii has higher leverage and is more influential than DC.",correct = TRUE))
```

### 2.

The scatterplot below shows the relationship between socioeconomic status measured as the percentage of 
children in a neighborhood receiving reduced-fee lunches at school (lunch) and bike helmet use 
measured as the percentage of bike riders in the neighborhood wearing helmets (helmet). The equation of the 
regression line is
<center>
helmet = 47.49 - 0.54 * lunch
</center>
and the $R^2$ is 72%.

```{r fig3}
grid::grid.raster(jpeg::readJPEG("fig3.jpg"))
```

```{r q2}
question("Which of the following is true?",
         answer('Neighborhoods where no students receive reduced-fee lunches are expected on average to 
         have 47.49% of bike riders wearing helmets.',correct = TRUE),
         answer("Decreasing the percentage of children receiving reduced-fee lunches 
         at school by 5% will increase the percentage of bike riders wearing helmets in that neighborhood 
         by 2.7%."),
         answer("The correlation coefficient is 0.85."),
         answer("72% of the percentage of children receiving reduced-fee lunches at school can be 
         accurately predicted by the model."))
```

### 3.

<b>The model below is for predicting the heart weight (in g) of cats 
from their gender (female and male). The coefficients are estimated 
using a dataset of 144 domestic cats.</b>

```{r fig4}
grid::grid.raster(jpeg::readJPEG("fig4.jpg"))
```

```{r q3}
question("Which of the following is false?",
         answer("The expected heart weight for female cats is 9.2 grams, on average."),
         answer("On average, male cats are expected to have hearts that weigh 2.12 grams more than the
                hearts of female cats."),
         answer("Because $\\mathbb{P}(>|t|)=0$ for the gender variable, we can say 
                that gender is not a significant predictor of heart weight in cats.",correct = TRUE),
         answer("Gender is a significant predictor of heart weight in cats."))
```

### 4.

<b>We fit a linear regression model for predicting the best used price 
of 23 GMC pickup trucks from their list price, both measured in 
thousands.</b>

```{r fig5}
grid::grid.raster(jpeg::readJPEG("fig5.jpg"))
```

```{r q4}
question("Which of the following is false based on this model output?",
         answer("For each additional $1,000 in the list price of a GMC pickup truck we would expect the 
         best used price to be higher on average by $850."),
         answer("The linear model is 
         $\\widehat{best\\_used\\_price} = 0.43 + 0.85\\cdot list\\_price$"),
         answer("The intercept is meaningless in this context."),
         answer("The 95% confidence interval for the slope can be calculated as 0.85±84.7×0.01",
                correct = TRUE),
         answer("List price is a significant predictor of the best used price."))
```

<b>Answer Question 5, 6 and 7 based on the information below:

Body fat percentage can be complicated to estimate, while variables such age, height, weight, and
measurements of various body parts are easy to measure. Based on data on body fat percentage and other
various easy to obtain measurements, we develop a model to predict body fat percentage based on the 
following variables:

-age (years)  - abdomen circumference (cm)   - forearm circumference (cm)

-wight (pounds)  - hip circumference (cm)     - wrist circumference (cm)

-neck circumference (cm)    - thigh circumference (cm)

The plot below shows the relationship between each of these variables and body fat percentage (the
response variable) as well as the correlation coefficients between these variables:</b>

```{r fig6}
grid::grid.raster(png::readPNG("fig6.png"))
```

<b>And the following are the model outputs associated with this analysis:</b>

```{r fig7}
grid::grid.raster(png::readPNG("fig7.png"))
```

<i>Source: Penrose, K., Nelson, A., and Fisher, A. (1985), Generalized Body Composition Prediction 
Equation for Men Using Simple Measurement Techniques, Medicine and Science in Sports and Exercise, 7(2), 
189.</i>

### 5.

```{r q5}
question("Which of the following is not supported by information provided in the model outputs above?",
         answer("All else held constant, people with wider hips tend to have lower body fat
                percentages."),
         answer("Wrist circumference is the most significant predictor of body fat percentage since the 
                slope associated with this variable has the highest magnitude.",correct = TRUE),
         answer("The sample size is 252."),
         answer("All else held constant, for each additional cm the forearm circumference is higher, body 
                fat percentage is expected to be higher by 0.483 percentage points."),
         answer("The F-test for the significance of the model overall suggests that at least one of the 
                slope coefficients is significantly different than 0."))
```

### 6.

```{r q6}
question("Do these data provide convincing evidence that age and body fat percentage are significantly 
         positively associated?  Why or why not? Use quantitative information based on the model output to
         support your answer, and make sure to note the p-value you use to make this decision.",
         answer("Yes, the p-value for testing for a positive correlation between age and body fat 
         percentage is 0.039. Since the p-value is small we reject the null hypothesis of no 
         relationship."),
         answer("Yes, the p-value for testing for a positive correlation between age and body fat 
         percentage is 0.039 / 2 = 0.0195. Since the p-value is small we reject the null hypothesis of no 
         relationship.",correct = TRUE),
         answer("Yes, the p-value for testing for a positive correlation between age and body fat 
         percentage is 2e$^{-16}$. Since the p-value is small we reject the null hypothesis of no 
         relationship."),
         answer("Yes, the p-value for testing for a positive correlation between age and body fat 
         percentage is 0.000. Since the p-value is small we reject the null hypothesis of no 
         relationship."))
```

### 7.

```{r q7}
question("Construct a 95% confidence interval for the slope of abdomen circumference and interpret it in 
         context of the data.",
         answer("(0.745, 1.009); All else held constant, for each additional percentage point increase in 
         body fat, abdomen circumference is expected to be higher by 0.745 to 1.009 cm."),
         answer("(-0.00539, 1.75); All else held constant, for each additional cm in abdomen 
         circumference, body fat percentage is expected to change by -0.00539 to 1.75 percentage
         points."),
         answer("(0.745, 1.009); All else held constant, for each additional cm in abdomen circumference, 
         body fat percentage is expected to be higher by 0.745 to 1.009 percentage points.",
         correct = TRUE),
         answer("(0.00539, 0.88239); All else held constant, for each additional cm in abdomen
         circumference, body fat percentage is expected to be higher by 0.00539 to 0.88239 percentage
         points."))
```

```{r q7a,exerice = TRUE}
## make computations 

```

### 8.

```{r q8}
question("True/False: Outliers should always be removed from the data set prior to final analysis.",
         answer("False; we only remove outliers after checking to make sure doing so drastically improves 
         model fit."),
         answer("True; outliers distort model fit and must be removed to assure reliable results."),
         answer("False; we only remove outliers if we have very good justification that suggests that 
         removing the outlier is appropriate.",correct = TRUE))
```