---
title: "Quiz 2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE,comment = '')
```
<style>body{text-align: justify}</style>
### 1.

```{r q1}
question("A study suggests that the average college student spends 2 hours per 
         week communicating with others online. You believe that this is an 
         underestimate and decide to collect your own sample for a hypothesis 
         test. You randomly sample 60 students from your dorm and find that on 
         average they spent 3.5 hours a week communicating with others online. 
         Which of the following is the correct set of hypotheses for this 
         scenario?",
         answer("$\\mathcal{H}_{0}:\\bar{x}=2$</br>$\\mathcal{H}_{a}:\\bar{x}<2$"),
         answer("$\\mathcal{H}_{0}:\\mu=2$</br>$\\mathcal{H}_{a}:\\mu<2$"),
         answer("$\\mathcal{H}_{0}:\\mu=2$</br>$\\mathcal{H}_{a}:\\mu>2$",correct = TRUE),
         answer("$\\mathcal{H}_{0}:\\bar{x}=2$</br>$\\mathcal{H}_{a}:\\bar{x}>2$"),
         answer("$\\mathcal{H}_{0}:\\mu=3.5$</br>$\\mathcal{H}_{a}:\\mu<3.5$"))
```

### 2.

```{r q2}
question("Which of the following is the correct definition of the p-value?",
         answer("$\\mathbb{P}(\\mathcal{H}_{0} true |\\text{observed sample statistic})$"),
         answer("$\\mathbb{P}(\\mathcal{H}_{0} true | \\mathcal{H}_{a} false)$"),
         answer("$\\mathbb{P}(\\text{observed or more extreme sample statistic}|\\mathcal{H}_{0} true)$",
                correct = TRUE),
         answer("$\\mathbb{P}(\\text{observed sample statistic}|\\mathcal{H}_{0} true)$"))
```

### 3.

```{r q3}
question("Two-sided alternative hypotheses are phrased in terms of:",
         answer("< or >"),answer("$\\neq$",correct = TRUE),
         answer("$\\leq$ or $\\geq$"),answer("$\\approx$ or ="))
```

### 4.

```{r q4}
question("You set up a two-sided hypothesis test for a population mean $\\mu$ 
         with a null hypothesis of $\\mathcal{H}_{0}: \\mu=100$. You chose a significance 
         level of $\\alpha=0.05$. The p-value calculated from the data is 
         0.12, and hence you failed to reject the null hypothesis. Suppose that 
         after your analysis was completed and published, an expert informed you 
         that the true value of $\\mu$ is 104. How would you describe the result of your analysis?",
         answer("A Type 2 error was made because you failed to reject the null hypothesis but $\\mu$ is
         really not equal to 100.",correct = TRUE),
         answer("You did not make a Type 1 or Type 2 error."),
         answer("A Type 1 error was made because you failed to reject the null hypothesis but $\\mu$ is
                really not equal to 100."))
```

### 5.

```{r q5}
question("A statistician is studying blood pressure levels of Italians in the 
         age range 75-80. The following is some information about her study:
         The data were collected by responses to a survey conducted by email, 
         and no measures were taken to get information from those who did not 
         respond to the initial survey email.</br>
         The sample observations only make up about 4% of the population.
         The sample size is 2,047.</br>
         The distribution of sample observations is skewed - the skew is easy to see, although not very 
         extreme.</br>
         The researcher is ready to use the Central Limit Theorem (CLT) in the main part of her analysis.
         Which aspect of the her study is most likely to prevent her from using the CLT?",
         answer("(I), because the sample may not be random and hence observations may not be 
                independent.",correct = TRUE),
         answer("(II), because she only has data from a small proportion of the whole population."),
         answer("(III), because the sample size is too small compared to all Italians in the age range 
         75-80."),
         answer("(IV), because there is some skew in the sample distribution."))
```

### 6.

```{r q6}
question("SAT scores are distributed with a mean of 1,500 and a standard deviation of 300. You are
         interested in estimating the average SAT score of first year students at your college. If you 
         would like to limit the margin of error of your 95% confidence interval to 25 points, at least 
         how many students should you sample?",
         answer("392"),answer("393"),answer("553"),answer("554",correct = TRUE),answer("13,830"))
```

```{r q6a,exercise = TRUE}
## make computations here

```

```{r q6a-solutions}
## ME = qnorm(*) * SE
ceiling((qnorm(.975) * (300/25))^2)
```

### 7.

```{r q7}
question("The significance level in hypothesis testing is the probability of",
         answer("rejecting a null hypothesis"),
         answer("rejecting an alternative hypothesis"),
         answer("rejecting a true null hypothesis",correct = TRUE),
         answer("failing to reject a false null hypothesis"),
         answer("failing to reject a true null hypothesis"))
```

### 8.

<b>Researchers investigating characteristics of gifted children 
collected data from schools in a large city on a random sample of 
thirty-six children who were identified as gifted children soon after 
they reached the age of four. The following histogram shows the 
distribution of the ages (in months) at which these children first 
counted to 10 successfully. Also provided are some sample statistics.

Suppose you read online that children first count to 10 successfully when they 
are 32 months old, on average. You perform a hypothesis test evaluating 
whether the average age at which gifted children first count to 10 is 
different than the general average of 32 months. What is the p-value of 
the hypothesis test?</b>

```{r fig,fig.align = 'center'}
grid::grid.raster(jpeg::readJPEG('fig.jpg'))
```
```{r q8}
question("Choose the closest answer.",
         answer("0.9656"),answer("0.9312"),answer("0.7183"),answer("0.0344"),
         answer("0.0688",correct = TRUE))
```

```{r q8a,exercise = TRUE}
## make computations here

```

```{r q8a-solution}
pnorm(30.69,32,4.31/sqrt(36)) * 2
```