---
title: "Quiz 2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

### 1.

```{r q1}
question("Which of the below data sets has the highest standard deviation? You do not need to 
         calculate the exact standard deviations to answer this question.",
         answer("0,1,1,1,1,1,2"),
         answer("0,100,200,300,400,500,600",correct = TRUE),
         answer("0, 25, 25, 25, 25, 25, 25"),
         answer("0,1,2,3,4,5,6"))
```

### 2.

```{r q2}
question("The distribution of housing prices in a country where 25% of the houses cost below 
         $350,000, 50% of the houses cost below $450,000, 75% of the houses cost below $1,000,000
         and there are a meaningful number of houses that cost more than $6,000,000 is most likely
         :",
         answer("right skewed",correct = TRUE),
         answer("symmetric"),
         answer("uniform"),
         answer("left skewed"))
```

### 3.

<b>Based on the relative frequency histogram below,</b>

```{r image, fig.align='center'}
jpeg::readJPEG("figure.jpg") -> x
grid::grid.raster(x)
```

```{r q3}
question("which of the following statements is supported by the plot?",
         answer("The mean of the distribution is smaller than its median."),
         answer("There are no outliers in the distribution."),
         answer("It is not possible to estimate the median without knowing the sample size."),
         answer("The IQR of the distribution is roughly 10.",correct = TRUE),
         answer("The distribution is multimodal."))
```

### 4.

```{r q4}
question("A recent housing survey was conducted to determine the price of a typical home in a
         city that is mostly middle-class, with one very expensive suburb. The mean price of a 
         house in this city is roughly $650,000. Which of the following statements is most likely
         to be true?",
         answer("There are about as many houses in this city that cost more than $650,000 than 
         less than this amount."),
         answer("We need to know the standard deviation to answer this question"),
         answer("Majority of houses in this city cost more than $650,000."),
         answer("Majority of houses in this city cost less than $650,000.",correct = TRUE))
```

### 5.

<b>Phi Delta Kappa (PDK) is an international professional organization for educators that, in
collaboration with Gallup, has been conducting polls on the public’s attitudes toward the public
schools since 1969. The following was one of the questions on the 2011 poll:

”Most teachers in the nation now belong to unions or associations that bargain over salaries,
working conditions, and the like. Has unionization, in your opinion, helped, hurt, or made no
difference in the quality of public school education in the United States?”. The respondents’
answers broken down by party affiliation are shown below</b>

```{r figure 2,fig.align = 'center',out.width = "50%"}
jpeg::readJPEG("figure2.jpg") -> x
grid::grid.raster(x)
```

```{r q5}
question("Which of the following statements is most justified by these data?",
         answer("14% of Republicans and 58% of Democrats think that teachers belonging to unions 
         or bargaining associations helped the quality of public school education in the United 
         States."),
         answer("The results of the survey suggest a relationship between opinion on teachers 
         belonging to unions or bargaining associations and political party affiliation.",
         correct = TRUE),
         answer("The results of the survey suggest that opinion on teachers belonging to unions 
         or bargaining associations and political party affiliation appear to be independent."),
         answer("A histogram or a box plot would be useful for investigating if distribution of 
         opinion on teachers belonging to unions or bargaining associations varies by political 
         party affiliation."))
```

### 6.

<b>Professors regularly give two versions of an exam. The professor may also provide summary
statistics for each version. Suppose the following summary is provided:</b>


```{r figure 3,fig.align = 'center',out.width = "50%"}
jpeg::readJPEG("figure3.jpg") -> x
grid::grid.raster(x)
```

```{r q6}
question("A student who took Version A says that he should get an extra point because his exam 
         was harder as evidenced by the lower mean score for Version A, as shown by the mean 
         score. Does the student have a good argument? Pick the best answer below.",
         answer("No. The median of Version A is higher."),
         answer("No. The average scores are relatively close when considering the spread of the 
         distributions. The difference might just be due to just chance.",correct = TRUE),
         answer("We need to know the shape of the distribution for each version to determine if 
         this argument is valid."),
         answer("Yes. Only 53 students took exam Version A while 65 students took exam Version 
                B."),
         answer("Yes. The difference in the exam scores means that there is a difference in 
         difficulty between the versions."),
         answer("We need to know the minimum and the maximum for each version to determine if 
         this argument is valid."))
```